%
% Bluebook Table 13a
%
% This file contains the contents of Table 13, of institutional and geographic
% terms.
\bb@abbrev{Academy}{Acad.}
\bb@abbrev{A.B.A.}{A.B.A.}
\bb@abbrev{ABA}{A.B.A.}
\bb@abbrev{American Bar Association}{A.B.A.}
\bb@abbrev{American Law Institute}{A.L.I.}
\bb@abbrev{Central}{Cent.}
\bb@abbrev{Chartered Life Underwriters}{C.L.U.}
\bb@abbrev{College}{C.}
\bb@abbrev{East}{E.}
\bb@abbrev{Eastern}{E.}
\bb@abbrev{Institute}{Inst.}
\bb@abbrev{Law School}{L. Sch.} % To ensure the "Law" is part of institution
\bb@abbrev{North}{N.}
\bb@abbrev{Northern}{N.}
\bb@abbrev{Pacific}{Pac.}
\bb@abbrev{School}{Sch.}
\bb@abbrev{Southern}{S.}
\bb@abbrev{South}{S.}
\bb@abbrev{State}{St.}
\bb@abbrev{United States}{U.S.}
\bb@abbrev{University}{U.}
\bb@abbrev{Universities}{U.}
\bb@abbrev{West}{W.}
\bb@abbrev{Western}{W.}
%
% Inferred abbreviations of institution names.
\ifnum\bb@jrnabb@inferlvl>\z@
\bb@abbrev{American Society Composers Authors \& Publishers}{ASCAP}
\bb@abbrev{Adelaide}{Adel.}
\bb@abbrev{Air Force}{A.F.}
\bb@abbrev{Albany}{Alb.}
\bb@abbrev{Boston College}{B.C.}
\bb@abbrev{Boston University}{B.U.}
\bb@abbrev{Buffalo}{Buff.}
\bb@abbrev{Brigham Young University}{BYU}
\bb@abbrev{Brooklyn}{Brook.}
\bb@abbrev{Capital University}{Cap. U.}
\bb@abbrev{Catholic University}{Cath. U.}
\bb@abbrev{Chapman}{Chap.}
\bb@abbrev{Cleveland}{Clev.}
\bb@abbrev{Columbia}{Colum.}
\bb@abbrev{Cumberland}{Cumb.}
\bb@abbrev{Denver}{Denv.}
\bb@abbrev{Dickinson}{Dick.}
% Must come before "District Columbia"
\bb@abbrev{University District Columbia David Clarke School Law}{UDC/DCSL}
\bb@abbrev{District of Columbia}{D.C.}
\bb@abbrev{District Columbia}{D.C.}
\bb@abbrev{Duquesne}{Duq.}
\bb@abbrev{Federal Circuit}{Fed. Cir.}
\bb@abbrev{George Mason}{Geo. Mason}
\bb@abbrev{George Washington}{Geo. Wash.}
\bb@abbrev{Georgetown}{Geo.}
\bb@abbrev{Gonzaga}{Gonz.}
\bb@abbrev{Harvard}{Harv.}
\bb@abbrev{Houston}{Hous.}
\bb@abbrev{John Marshall}{J. Marshall}
\bb@abbrev{Loyola}{Loy.}
\bb@abbrev{Marquette}{Marq.}
\bb@abbrev{Melbourne}{Melb.}
\bb@abbrev{University Memphis}{U. Mem.}
\bb@abbrev{Northwestern}{Nw.}
\bb@abbrev{Pepperdine}{Pepp.}
\bb@abbrev{Pittsburgh}{Pitt.}
\bb@abbrev{Richmond}{Rich.}
\bb@abbrev{Rocky Mountain}{Rocky Mtn.}
\bb@abbrev{Rutgers-Camden}{Rutgers-Cam.}
\bb@abbrev{Saint Louis}{St. Louis}
\bb@abbrev{San Fernando Valley}{San Fern. V.}
\bb@abbrev{Southern Methodist University}{SMU}
\bb@abbrev{Southwestern}{Sw.}
\bb@abbrev{Stanford}{Stan.}
\bb@abbrev{Temple}{Temp.}
\bb@abbrev{Thomas Jefferson}{T. Jefferson}
\bb@abbrev{Thomas M. Cooley}{T.M. Cooley}
\bb@abbrev{Thurgood Marshall}{T. Marshall}
\bb@abbrev{Tulane}{Tul.}
\bb@abbrev{Vanderbilt}{Vand.}
\bb@abbrev{Valparaiso}{Val.}
\bb@abbrev{Villanova}{Vill.}
\bb@abbrev{Wall Street}{Wall St.}
\bb@abbrev{William and Mary}{Wm. and Mary} % Ampersand will be added later
\bb@abbrev{William Mitchell}{Wm. Mitchell}
\bb@abbrev{University Cincinnati}{U. Cin.}
\bb@abbrev{University California}{U.C.}
\bb@abbrev{University West Los Angeles}{UWLA}
\bb@abbrev{University Toledo}{U. Tol.}
\bb@abbrev{University Detroit}{U. Det.}
\bb@abbrev{Puertorriqueno}{P.R.}
\bb@abbrev{Universidad}{U.}
\fi
\ifnum\bb@jrnabb@inferlvl>\@ne
    \bb@abbrev{George}{Geo.}
    \bb@abbrev{William}{Wm.}
    \bb@abbrev{Toledo}{Tol.}
\fi
