%
% Bluebook Table 13.
%
% This file contains abbreviations for non-institutional title words.
% Institutional words are contained in the file bbtbl13a.
% Full journal abbreviations are contained in bbtbl13b.
%
%
%
\bb@abbrev{Academic}{Acad.}
\bb@abbrev{Account}{Acct.}
\bb@abbrev{Accountancy}{Acct.}
\bb@abbrev{Accountant}{Acct.}
\bb@abbrev{Accountants}{Acct.}
\bb@abbrev{Accounting}{Acct.}
\bb@abbrev{Administration}{Admin.}
\bb@abbrev{Administrative}{Admin.}
\bb@abbrev{Administrator}{Admin.}
\bb@abbrev{Advocacy}{Advoc.}
\bb@abbrev{Advocate}{Advoc.}
\bb@abbrev{Affairs}{Aff.}
\bb@abbrev{Africa}{Afr.}
\bb@abbrev{African}{Afr.}
\bb@abbrev{Agricultural}{Agric.}
\bb@abbrev{Agriculture}{Agric.}
\bb@abbrev{America}{Am.}
\bb@abbrev{Americas}{Am.}
\bb@abbrev{American}{Am.}
\bb@abbrev{American Law Reports}{A.L.R.}
\bb@abbrev{and}{\&}
%\bb@abbrev{&}{\PackageWarning\bb@pkgname{Do not use ampersands in journal names}\&}
%\bb@abbrev{\&}{\PackageWarning\bb@pkgname{Do not use ampersands in journal names}\&}
\bb@abbrev{Annual}{Ann.}
\bb@abbrev{Appellate}{App.}
\bb@abbrev{Arbitration}{Arb.}
\bb@abbrev{Arbitrators}{Arb.}
\bb@abbrev{Association}{Ass'n}
\bb@abbrev{Attorney}{Att'y}
\bb@abbrev{Attorneys}{Att'ys}
\bb@abbrev{Bankruptcy}{Bankr.}
\bb@abbrev{Bar}{B.}
\bb@abbrev{Behavior}{Behav.}
\bb@abbrev{Behavioral}{Behav.}
\bb@abbrev{British}{Brit.}
\bb@abbrev{Bulletin}{Bull.}
\bb@abbrev{Business}{Bus.}
\bb@abbrev{Children}{Child.}
\bb@abbrev{Children's}{Child.}
\bb@abbrev{Chronicle}{Chron.}
\bb@abbrev{Civil}{Civ.}
\bb@abbrev{Civil Liberty}{C.L.}
\bb@abbrev{Civil Liberties}{C.L.}
\bb@abbrev{Civil Rights}{C.R.}
\bb@abbrev{Commentary}{Comment.}
\bb@abbrev{Commerce}{Com.}
\bb@abbrev{Commercial}{Com.}
\bb@abbrev{Communication}{Comm.}
\bb@abbrev{Communications}{Comm.}
\bb@abbrev{Comparative}{Comp.}
\bb@abbrev{Conference}{Conf.}
\bb@abbrev{Congressional}{Cong.}
\bb@abbrev{Constitution}{Const.}
\bb@abbrev{Constitutional}{Const.}
\bb@abbrev{Contemporary}{Contemp.}
\bb@abbrev{Contract}{Cont.}
\bb@abbrev{Contracts}{Cont.}
\bb@abbrev{Corporate}{Corp.}
\bb@abbrev{Corporation}{Corp.}
\bb@abbrev{Counsel}{Couns.}
\bb@abbrev{Conselor}{Couns.}
\bb@abbrev{Counselors}{Couns.}
\bb@abbrev{Counselor's}{Couns.}
\bb@abbrev{Court}{Ct.}
\bb@abbrev{Courts}{Cts.}
\bb@abbrev{Criminal}{Crim.}
\bb@abbrev{Defense}{Def.}
\bb@abbrev{Delinquency}{Delinq.}
\bb@abbrev{Development}{Dev.}
\bb@abbrev{Developments}{Dev.}
\bb@abbrev{Digest}{Dig.}
\bb@abbrev{Diplomacy}{Dipl.}
\bb@abbrev{Dispute}{Disp.}
\bb@abbrev{Economic}{Econ.}
\bb@abbrev{Economics}{Econ.}
\bb@abbrev{Economy}{Econ.}
\bb@abbrev{Education}{Educ.}
\bb@abbrev{Educational}{Educ.}
\bb@abbrev{Employee}{Emp.}
\bb@abbrev{Employment}{Emp.}
\bb@abbrev{English}{Eng.}
\bb@abbrev{Entertainment}{Ent.}
\bb@abbrev{Environment}{Env't}
\bb@abbrev{Environmental}{Envtl.}
\bb@abbrev{Estate}{Est.}
\bb@abbrev{Estates}{Est.}
\bb@abbrev{Europe}{Eur.}
\bb@abbrev{European}{Eur.}
\bb@abbrev{Faculty}{Fac.}
\bb@abbrev{Family}{Fam.}
\bb@abbrev{Federal}{Fed.}
\bb@abbrev{Federation}{Fed'n}
\bb@abbrev{Finance}{Fin.}
\bb@abbrev{Financial}{Fin.}
\bb@abbrev{Fortnightly}{Fort.}
\bb@abbrev{Forum}{F.}
\bb@abbrev{Foundation}{Found.}
\bb@abbrev{Foundations}{Found.}
\bb@abbrev{General}{Gen.}
\bb@abbrev{Government}{Gov't}
\bb@abbrev{Hispanic}{Hisp.}
\bb@abbrev{Historical}{Hist.}
\bb@abbrev{History}{Hist.}
\bb@abbrev{Hospital}{Hosp.}
\bb@abbrev{Human}{Hum.}
\bb@abbrev{Humanity}{Human.}
\bb@abbrev{Humanities}{Human.}
\bb@abbrev{Immigration}{Immigr.}
\bb@abbrev{Independent}{Indep.}
\bb@abbrev{Industrial}{Indus.}
\bb@abbrev{Information}{Info.}
\bb@abbrev{Injury}{Inj.}
\bb@abbrev{Insurance}{Ins.}
\bb@abbrev{Intellectual}{Intell.}
\bb@abbrev{Interdisciplinary}{Interdisc.}
\bb@abbrev{Interest}{Int.}
\bb@abbrev{International}{Int'l}
\bb@abbrev{Journal}{J.}
\bb@abbrev{Judicial}{Jud.}
\bb@abbrev{Justice}{Just.}
\bb@abbrev{Juvenile}{Juv.}
\bb@abbrev{Labor}{Lab.}
\bb@abbrev{Labour}{Lab.}
% \bb@abbrev{\bb@jrnabb@markstart Law}{Law}
\bb@abbrev{Law}{L.}
\bb@abbrev{Lawyer}{Law.}
\bb@abbrev{Lawyers}{Law.}
% There is a problem with the following two entries, in that because they are
% multiple-word abbreviations (due to the apostrophe), they get abbreviated in
% the multiple-word round to "Law.", which then gets abbreviated again in the
% single-word round to "L..". The hackish way to avoid this (which is not ideal)
% is to instead abbreviate it to something that, after both rounds, turns into
% "Law.".
\bb@abbrev{Lawyer's}{Lawyer}
\bb@abbrev{Lawyers'}{Lawyer}
\bb@abbrev{Legislation}{Legis.}
\bb@abbrev{Legislative}{Legis.}
\bb@abbrev{Library}{Libr.}
\bb@abbrev{Librarian}{Libr.}
\bb@abbrev{Libraries}{Libr.}
\bb@abbrev{Litigation}{Litig.}
\bb@abbrev{Local}{Loc.}
\bb@abbrev{Magazine}{Mag.}
\bb@abbrev{Management}{Mgmt.}
\bb@abbrev{Maritime}{Mar.}
\bb@abbrev{Medical}{Med.}
\bb@abbrev{Medicine}{Med.}
\bb@abbrev{Mineral}{Min.}
\bb@abbrev{Municipal}{Mun.}
\bb@abbrev{National}{Nat'l}
\bb@abbrev{Natural}{Nat.}
\bb@abbrev{Negligence}{Negl.}
\bb@abbrev{(new series)}{(n.s.)}
\bb@abbrev{Newsletter}{Newsl.}
\bb@abbrev{Office}{Off.}
\bb@abbrev{Order}{Ord.}
\bb@abbrev{Organization}{Org.}
\bb@abbrev{Patent}{Pat.}
\bb@abbrev{Personal}{Pers.}
\bb@abbrev{Perspective}{Persp.}
\bb@abbrev{Perspectives}{Persp.}
\bb@abbrev{Philosophy}{Phil.}
\bb@abbrev{Philosophical}{Phil.}
\bb@abbrev{Planning}{Plan.}
\bb@abbrev{Policy}{Pol'y}
\bb@abbrev{Political}{Pol.}
\bb@abbrev{Politics}{Pol.}
\bb@abbrev{Practical}{Prac.}
\bb@abbrev{Practice}{Prac.}
\bb@abbrev{Practitioner}{Prac.}
\bb@abbrev{Practitioners}{Prac.}
\bb@abbrev{Probate}{Prob.}
\bb@abbrev{Problems}{Probs.}
\bb@abbrev{Proceedings}{Proc.}
\bb@abbrev{Procedure}{Proc.}
\bb@abbrev{Profession}{Prof.}
\bb@abbrev{Professional}{Prof.}
\bb@abbrev{Property}{Prop.}
\bb@abbrev{Psychology}{Psychol.}
\bb@abbrev{Psychological}{Psychol.}
\bb@abbrev{Public}{Pub.}
\bb@abbrev{Quarterly}{Q.}
\bb@abbrev{Record}{Rec.}
\bb@abbrev{Referees}{Ref.}
\bb@abbrev{Register}{Reg.}
\bb@abbrev{Regulation}{Reg.}
\bb@abbrev{Regulatory}{Reg.}
\bb@abbrev{Relations}{Rel.}
\bb@abbrev{Report}{Rep.}
\bb@abbrev{Reports}{Rep.}
\bb@abbrev{Reporter}{Rep.}
\bb@abbrev{Reproduction}{Reprod.}
\bb@abbrev{Reproductive}{Reprod.}
\bb@abbrev{Research}{Res.}
\bb@abbrev{Reserve}{Res.}
\bb@abbrev{Resolution}{Resol.}
\bb@abbrev{Responsibility}{Resp.}
\bb@abbrev{Review}{Rev.}
\bb@abbrev{Rights}{Rts.}
\bb@abbrev{Science}{Sci.}
\bb@abbrev{Sciences}{Sci.}
\bb@abbrev{Scientific}{Sci.}
\bb@abbrev{Scottish}{Scot.}
\bb@abbrev{Section}{Sec.}
\bb@abbrev{Securities}{Sec.}
\bb@abbrev{Sentencing}{Sent'g}
\bb@abbrev{Social}{Soc.}
\bb@abbrev{Society}{Soc'y}
\bb@abbrev{Sociological}{Soc.}
\bb@abbrev{Sociology}{Soc.}
\bb@abbrev{Solicitor}{Solic.}
\bb@abbrev{Solicitor's}{Solic.}
\bb@abbrev{Solicitors}{Solic.}
\bb@abbrev{Solicitors'}{Solic.}
\bb@abbrev{Statistics}{Stat.}
\bb@abbrev{Statistical}{Stat.}
\bb@abbrev{Studies}{Stud.}
\bb@abbrev{Survey}{Surv.}
\bb@abbrev{Symposium}{Symp.}
\bb@abbrev{System}{Sys.}
\bb@abbrev{Taxation}{Tax'n}
\bb@abbrev{Teacher}{Tchr.}
\bb@abbrev{Teachers}{Tchrs.}
\bb@abbrev{Technique}{Tech.}
\bb@abbrev{Technology}{Tech.}
\bb@abbrev{Telecommunications}{Telecomm.}
\bb@abbrev{Transnational}{Transnat'l}
\bb@abbrev{Transportation}{Transp.}
\bb@abbrev{Tribune}{Trib.}
\bb@abbrev{Trust}{Tr.}
\bb@abbrev{Trusts}{Tr.}
\bb@abbrev{Urban}{Urb.}
\bb@abbrev{Utility}{Util.}
\bb@abbrev{Utilities}{Util.}
\bb@abbrev{Week}{Wk.}
\bb@abbrev{Weekly}{Wkly.}
\bb@abbrev{Yearbook}{Y.B.}
\bb@abbrev{Year Book}{Y.B.}
%
% Inferred abbreviations
%
\ifnum\bb@jrnabb@inferlvl>\@ne
    \bb@abbrev{Catholic}{Cath.}
    \bb@abbrev{Cosmetic}{Cosm.}
    \bb@abbrev{Department}{Dep't}
    \bb@abbrev{Inequality}{Ineq.}
    \bb@abbrev{Investments}{Inv.}
    \bb@abbrev{Investment}{Inv.}
    \bb@abbrev{Investors}{Inv.}
    \bb@abbrev{Investor}{Inv.}
    \bb@abbrev{Juridical}{Jurid.}
    \bb@abbrev{Liabilities}{Liab.}
    \bb@abbrev{Liability}{Liab.}
    \bb@abbrev{Matrimonial}{Matrim.}
    \bb@abbrev{Nationalities}{Nat'lities}
    \bb@abbrev{Nationality}{Nat'lity}
    \bb@abbrev{Negotiations}{Negot.}
    \bb@abbrev{Negotiation}{Negot.}
    \bb@abbrev{Products}{Prod.}
    \bb@abbrev{Uniform Commercial Code}{UCC}
    \bb@abbrev{Supreme Court}{Sup. Ct.}
    \bb@abbrev{Revista}{Rev.}
    \bb@abbrev{Juridica}{Jur.}
    \bb@abbrev{Derecho}{Der.}
\fi
\endinput
