\bb@abbrev{Academies}{Acads.}
\bb@abbrev{Academy}{Acad.}
\bb@abbrev{Administration}{Admin.}
\bb@abbrev{Administrations}{Admins.}
\bb@abbrev{Administrative}{Admin.}
\bb@abbrev{Administrator}{Adm'r}
\bb@abbrev{Administrators}{Adm'rs}
\bb@abbrev{Administratrixes}{Adm'xs}
\bb@abbrev{Administratrices}{Adm'xs}
\bb@abbrev{Administratrix}{Adm'x}
\bb@abbrev{Advertising}{Adver.}
\bb@abbrev{Agricultural}{Agric.}
\bb@abbrev{Agriculture}{Agric.}
\bb@abbrev{Agricultures}{Agrics.}
\bb@abbrev{America}{Am.}
\bb@abbrev{American}{Am.}
\bb@abbrev{Associate}{Assoc.}
\bb@abbrev{Associates}{Assocs.}
\bb@abbrev{Association}{Ass'n}
\bb@abbrev{Associations}{Ass'ns}
\bb@abbrev{Atlantic}{Atl.}
\bb@abbrev{Authorities}{Auths.}
\bb@abbrev{Authority}{Auth.}
\bb@abbrev{Automobile}{Auto.}
\bb@abbrev{Automobiles}{Autos.}
\bb@abbrev{Automotive}{Auto.}
\bb@abbrev{Automotives}{Autos.}
\bb@abbrev{Avenue}{Ave.}
\bb@abbrev{Avenues}{Aves.}
\bb@abbrev{Bankruptcies}{Bankrs.}
\bb@abbrev{Bankruptcy}{Bankr.}
\bb@abbrev{Board}{Bd.}
\bb@abbrev{Boards}{Bds.}
\bb@abbrev{Broadcast}{Broad.}
\bb@abbrev{Broadcasting}{Broad.}
\bb@abbrev{Broadcasts}{Broads.}
\bb@abbrev{Brotherhood}{Bhd.}
\bb@abbrev{Brotherhoods}{Bhds.}
\bb@abbrev{Brothers}{Bros.}
\bb@abbrev{Building}{Bldg.}
\bb@abbrev{Buildings}{Bldgs.}
\bb@abbrev{Business}{Bus.}
\bb@abbrev{Businesses}{Buss.}
\bb@abbrev{Casualties}{Cass.}
\bb@abbrev{Casualty}{Cas.}
\bb@abbrev{Center}{Ctr.}
\bb@abbrev{Centers}{Ctrs.}
\bb@abbrev{Central}{Cent.}
\bb@abbrev{Centre}{Ctr.}
\bb@abbrev{Centres}{Ctrs.}
\bb@abbrev{Chemical}{Chem.}
\bb@abbrev{Chemicals}{Chems.}
\bb@abbrev{Coalition}{Coal.}
\bb@abbrev{College}{Coll.}
\bb@abbrev{Colleges}{Colls.}
\bb@abbrev{Commission}{Comm'n}
\bb@abbrev{Commissioner}{Comm'r}
\bb@abbrev{Commissioners}{Comm'rs}
\bb@abbrev{Commissions}{Comm'ns}
\bb@abbrev{Committee}{Comm.}
\bb@abbrev{Committees}{Comms.}
\bb@abbrev{Communication}{Commc'n}
\bb@abbrev{Communications}{Commc'ns}
\bb@abbrev{Communities}{Cmtys.}
\bb@abbrev{Community}{Cmty.}
\bb@abbrev{Companies}{Cos.}
\bb@abbrev{Company}{Co.}
\bb@abbrev{Compensation}{Comp.}
\bb@abbrev{Compensations}{Comps.}
\bb@abbrev{Condominium}{Condo.}
\bb@abbrev{Condominiums}{Condos.}
\bb@abbrev{Congress}{Cong.}
\bb@abbrev{Congresses}{Congs.}
\bb@abbrev{Congressional}{Cong.}
\bb@abbrev{Consolidated}{Consol.}
\bb@abbrev{Construction}{Constr.}
\bb@abbrev{Constructions}{Constrs.}
\bb@abbrev{Continental}{Cont'l}
\bb@abbrev{Cooperative}{Coop.}
\bb@abbrev{Cooperatives}{Coops.}
\bb@abbrev{Corporation}{Corp.}
\bb@abbrev{Corporations}{Corps.}
\bb@abbrev{Correctional}{Corr.}
\bb@abbrev{Corrections}{Corr.}
\bb@abbrev{Correction}{Corr.}
\bb@abbrev{Defense}{Def.}
\bb@abbrev{Defenses}{Defs.}
\bb@abbrev{Department}{Dep't}
\bb@abbrev{Departments}{Dep'ts}
\bb@abbrev{Detention}{Det.}
\bb@abbrev{Detentions}{Dets.}
\bb@abbrev{Development}{Dev.}
\bb@abbrev{Developments}{Devs.}
\bb@abbrev{Director}{Dir.}
\bb@abbrev{Directors}{Dirs.}
\bb@abbrev{Discount}{Disc.}
\bb@abbrev{Discounts}{Discs.}
\bb@abbrev{Distributing}{Distrib.}
\bb@abbrev{Distributor}{Distrib.}
\bb@abbrev{Distributors}{Distribs.}
\bb@abbrev{District}{Dist.}
\bb@abbrev{Districts}{Dists.}
\bb@abbrev{Division}{Div.}
\bb@abbrev{Divisions}{Divs.}
\bb@abbrev{East}{E.}
\bb@abbrev{Eastern}{E.}
\bb@abbrev{Economic}{Econ.}
\bb@abbrev{Economical}{Econ.}
\bb@abbrev{Economics}{Econ.}
\bb@abbrev{Economies}{Econs.}
\bb@abbrev{Economy}{Econ.}
\bb@abbrev{Education}{Educ.}
\bb@abbrev{Educational}{Educ.}
\bb@abbrev{Educations}{Educs.}
\bb@abbrev{Electric}{Elec.}
\bb@abbrev{Electrical}{Elec.}
\bb@abbrev{Electricities}{Elecs.}
\bb@abbrev{Electricity}{Elec.}
\bb@abbrev{Electronic}{Elec.}
\bb@abbrev{Electronics}{Elecs.}
\bb@abbrev{Engineer}{Eng'r}
\bb@abbrev{Engineering}{Eng'g}
\bb@abbrev{Engineerings}{Eng'gs}
\bb@abbrev{Engineers}{Eng'rs}
\bb@abbrev{Enterprise}{Enter.}
\bb@abbrev{Enterprises}{Enters.}
\bb@abbrev{Entertainment}{Entm't}
\bb@abbrev{Entertainments}{Entm'ts}
\bb@abbrev{Environment}{Env't}
\bb@abbrev{Environmental}{Envtl.}
\bb@abbrev{Environments}{Env'ts}
\bb@abbrev{Equalities}{Equals.}
\bb@abbrev{Equality}{Equal.}
\bb@abbrev{Equipment}{Equip.}
\bb@abbrev{Equipments}{Equips.}
\bb@abbrev{Examiner}{Exam'r}
\bb@abbrev{Examiners}{Exam'rs}
\bb@abbrev{Exchange}{Exch.}
\bb@abbrev{Exchanges}{Exchs.}
\bb@abbrev{Executor}{Ex'r}
\bb@abbrev{Executors}{Ex'rs}
\bb@abbrev{Executrices}{Ex'xs}
\bb@abbrev{Executrixes}{Ex'xs}
\bb@abbrev{Executrix}{Ex'x}
\bb@abbrev{Export}{Exp.}
\bb@abbrev{Exportation}{Exp.}
\bb@abbrev{Exportations}{Exps.}
\bb@abbrev{Exporter}{Exp.}
\bb@abbrev{Exporters}{Exps.}
\bb@abbrev{Exports}{Exps.}
\bb@abbrev{Federal}{Fed.}
\bb@abbrev{Federation}{Fed'n}
\bb@abbrev{Federations}{Fed'ns}
\bb@abbrev{Fidelities}{Fids.}
\bb@abbrev{Fidelity}{Fid.}
\bb@abbrev{Finance}{Fin.}
\bb@abbrev{Finances}{Fins.}
\bb@abbrev{Financial}{Fin.}
\bb@abbrev{Financials}{Fins.}
\bb@abbrev{Financing}{Fin.}
\bb@abbrev{Financings}{Fins.}
\bb@abbrev{Foundation}{Found.}
\bb@abbrev{Foundations}{Founds.}
\bb@abbrev{General}{Gen.}
\bb@abbrev{Generals}{Gens.}
\bb@abbrev{Government}{Gov't}
\bb@abbrev{Governments}{Gov'ts}
\bb@abbrev{Guaranties}{Guars.}
\bb@abbrev{Guaranty}{Guar.}
\bb@abbrev{Hospital}{Hosp.}
\bb@abbrev{Hospitals}{Hosps.}
\bb@abbrev{Housing}{Hous.}
\bb@abbrev{Import}{Imp.}
\bb@abbrev{Importation}{Imp.}
\bb@abbrev{Importations}{Imps.}
\bb@abbrev{Importer}{Imp.}
\bb@abbrev{Importers}{Imps.}
\bb@abbrev{Imports}{Imps.}
\bb@abbrev{Incorporated}{Inc.}
\bb@abbrev{Indemnities}{Indems.}
\bb@abbrev{Indemnity}{Indem.}
\bb@abbrev{Independent}{Indep.}
\bb@abbrev{Independents}{Indeps.}
\bb@abbrev{Industrial}{Indus.}
\bb@abbrev{Industries}{Indus.}
\bb@abbrev{Industry}{Indus.}
\bb@abbrev{Information}{Info.}
\bb@abbrev{Institute}{Inst.}
\bb@abbrev{Institutes}{Insts.}
\bb@abbrev{Institution}{Inst.}
\bb@abbrev{Institutions}{Insts.}
\bb@abbrev{Insurance}{Ins.}
\bb@abbrev{International}{Int'l}
\bb@abbrev{Investment}{Inv.}
\bb@abbrev{Investments}{Invs.}
\bb@abbrev{Laboratories}{Labs.}
\bb@abbrev{Laboratory}{Lab.}
\bb@abbrev{Liabilities}{Liabs.}
\bb@abbrev{Liability}{Liab.}
\bb@abbrev{Limited}{Ltd.}
\bb@abbrev{Litigation}{Litig.}
\bb@abbrev{Litigations}{Litigs.}
\bb@abbrev{Machine}{Mach.}
\bb@abbrev{Machineries}{Machs.}
\bb@abbrev{Machinery}{Mach.}
\bb@abbrev{Machines}{Machs.}
\bb@abbrev{Maintenance}{Maint.}
\bb@abbrev{Management}{Mgmt.}
\bb@abbrev{Managements}{Mgmts.}
\bb@abbrev{Manufacturer}{Mfr.}
\bb@abbrev{Manufacturers}{Mfrs.}
\bb@abbrev{Manufacturing}{Mfg.}
\bb@abbrev{Maritime}{Mar.}
\bb@abbrev{Market}{Mkt.}
\bb@abbrev{Marketing}{Mktg.}
\bb@abbrev{Markets}{Mkts.}
\bb@abbrev{Mechanic}{Mech.}
\bb@abbrev{Mechanical}{Mech.}
\bb@abbrev{Mechanicals}{Mechs.}
\bb@abbrev{Mechanics}{Mechs.}
\bb@abbrev{Medical}{Med.}
\bb@abbrev{Medicine}{Med.}
\bb@abbrev{Medicines}{Meds.}
\bb@abbrev{Memorial}{Mem'l}
\bb@abbrev{Memorials}{Mem'ls}
\bb@abbrev{Merchandise}{Merch.}
\bb@abbrev{Merchandising}{Merch.}
\bb@abbrev{Merchant}{Merch.}
\bb@abbrev{Merchants}{Merchs.}
\bb@abbrev{Metropolitan}{Metro.}
\bb@abbrev{Municipal}{Mun.}
\bb@abbrev{Mutual}{Mut.}
\bb@abbrev{National}{Nat'l}
\bb@abbrev{North}{N.}
\bb@abbrev{Northern}{N.}
\bb@abbrev{Northeast}{Ne.}
\bb@abbrev{Northeastern}{Ne.}
\bb@abbrev{Northwest}{Nw.}
\bb@abbrev{Northwestern}{Nw.}
\bb@abbrev{Number}{No.}
\bb@abbrev{Organization}{Org.}
\bb@abbrev{Organizations}{Orgs.}
\bb@abbrev{Organizing}{Org.}
\bb@abbrev{Pacific}{Pac.}
\bb@abbrev{Partnership}{P'ship}
\bb@abbrev{Partnerships}{P'ships}
\bb@abbrev{Person}{Pers.}
\bb@abbrev{Personal}{Pers.}
\bb@abbrev{Personnel}{Pers.}
\bb@abbrev{Persons}{Perss.}
\bb@abbrev{Pharmaceutical}{Pharm.}
\bb@abbrev{Pharmaceutics}{Pharm.}
\bb@abbrev{Preservation}{Pres.}
\bb@abbrev{Preservations}{Press.}
\bb@abbrev{Preserve}{Pres.}
\bb@abbrev{Preserves}{Press.}
\bb@abbrev{Probation}{Prob.}
\bb@abbrev{Probations}{Probs.}
\bb@abbrev{Product}{Prod.}
\bb@abbrev{Production}{Prod.}
\bb@abbrev{Productions}{Prods.}
\bb@abbrev{Products}{Prods.}
\bb@abbrev{Professional}{Prof'l}
\bb@abbrev{Professionals}{Prof'ls}
\bb@abbrev{Properties}{Props.}
\bb@abbrev{Property}{Prop.}
\bb@abbrev{Protection}{Prot.}
\bb@abbrev{Protections}{Prots.}
\bb@abbrev{Public}{Pub.}
\bb@abbrev{Publication}{Publ'n}
\bb@abbrev{Publications}{Publ'ns}
\bb@abbrev{Publics}{Pubs.}
\bb@abbrev{Publishing}{Publ'g}
\bb@abbrev{Publishings}{Publ'gs}
\bb@abbrev{Railroad}{R.R.}
\bb@abbrev{Railroads}{R.Rs.}
\bb@abbrev{Rail Road}{R.R.}
\bb@abbrev{Rail Roads}{R.Rs.}
\bb@abbrev{Railway}{Ry.}
\bb@abbrev{Railways}{Rys.}
\bb@abbrev{Refining}{Ref.}
\bb@abbrev{Regional}{Reg'l}
\bb@abbrev{Regionals}{Reg'ls}
\bb@abbrev{Rehabilitation}{Rehab.}
\bb@abbrev{Reproduction}{Reprod.}
\bb@abbrev{Reproductions}{Reprods.}
\bb@abbrev{Reproductive}{Reprod.}
\bb@abbrev{Resource}{Res.}
\bb@abbrev{Resources}{Res.}
\bb@abbrev{Restaurant}{Rest.}
\bb@abbrev{Restaurants}{Rests.}
\bb@abbrev{Retirement}{Ret.}
\bb@abbrev{Retirements}{Rets.}
\bb@abbrev{Road}{Rd.}
\bb@abbrev{Roads}{Rds.}
\bb@abbrev{Savings}{Sav.}
\bb@abbrev{School}{Sch.}
\bb@abbrev{Schools}{Sch.}
\bb@abbrev{Science}{Sci.}
\bb@abbrev{Sciences}{Scis.}
\bb@abbrev{Secretaries}{Sec'ys}
\bb@abbrev{Secretary}{Sec'y}
\bb@abbrev{Securities}{Sec.}
\bb@abbrev{Security}{Sec.}
\bb@abbrev{Service}{Serv.}
\bb@abbrev{Services}{Servs.}
\bb@abbrev{Shareholder}{S'holder}
\bb@abbrev{Shareholders}{S'holders}
\bb@abbrev{Social}{Soc.}
\bb@abbrev{Socials}{Socs.}
\bb@abbrev{Societies}{Soc'ys}
\bb@abbrev{Society}{Soc'y}
\bb@abbrev{South}{S.}
\bb@abbrev{Southern}{S.}
\bb@abbrev{Southeast}{Se.}
\bb@abbrev{Southeastern}{Se.}
\bb@abbrev{Southwest}{Sw.}
\bb@abbrev{Southwestern}{Sw.}
\bb@abbrev{Steamship}{S.S.}
\bb@abbrev{Steamships}{S.S.}
\bb@abbrev{Street}{St.}
\bb@abbrev{Streets}{Sts.}
\bb@abbrev{Subcommittee}{Subcomm.}
\bb@abbrev{Subcommittees}{Subcomms.}
\bb@abbrev{Sureties}{Surs.}
\bb@abbrev{Surety}{Sur.}
\bb@abbrev{System}{Sys.}
\bb@abbrev{Systems}{Sys.}
\bb@abbrev{Technologies}{Techs.}
\bb@abbrev{Technology}{Tech.}
\bb@abbrev{Telecommunication}{Telecomm.}
\bb@abbrev{Telecommunications}{Telecomms.}
\bb@abbrev{Telegraph}{Tel.}
\bb@abbrev{Telegraphs}{Tels.}
\bb@abbrev{Telephone}{Tel.}
\bb@abbrev{Telephones}{Tels.}
\bb@abbrev{Temporary}{Temp.}
\bb@abbrev{Township}{Twp.}
\bb@abbrev{Transcontinental}{Transcon.}
\bb@abbrev{Transport}{Transp.}
\bb@abbrev{Transportation}{Transp.}
\bb@abbrev{Transports}{Transps.}
\bb@abbrev{Trustee}{Tr.}
\bb@abbrev{Trustees}{Trs.}
\bb@abbrev{Turnpike}{Tpk.}
\bb@abbrev{Turnpikes}{Tpks.}
\bb@abbrev{Uniform}{Unif.}
\bb@abbrev{Uniforms}{Unifs.}
\bb@abbrev{Universities}{Univs.}
\bb@abbrev{University}{Univ.}
\bb@abbrev{Utilities}{Utils.}
\bb@abbrev{Utility}{Util.}
\bb@abbrev{Village}{Vill.}
\bb@abbrev{Villages}{Vills.}
\bb@abbrev{West}{W.}
\bb@abbrev{Western}{W.}
\bb@abbrev{and}{\&}
