%
% United States
%
\bb@abbrev{Alabama}{Ala.}
\bb@abbrev{American Samoa}{Am. Sam.}
\bb@abbrev{Arizona}{Ariz.}
\bb@abbrev{Arkansas}{Ark.}
\bb@abbrev{Baltimore}{Balt.}
\bb@abbrev{California}{Cal.}
\bb@abbrev{Canal Zone}{C.Z.}
\bb@abbrev{Chicago}{Chi.}
\bb@abbrev{Colorado}{Colo.}
\bb@abbrev{Connecticut}{Conn.}
\bb@abbrev{Delaware}{Del.}
\bb@abbrev{District of Columbia}{D.C.}
\bb@abbrev{Florida}{Fla.}
\bb@abbrev{Georgia}{Ga.}
\bb@abbrev{Hawaii}{Haw.}
\bb@abbrev{Illinois}{Ill.}
\bb@abbrev{Indiana}{Ind.}
\bb@abbrev{Kansas}{Kan.}
\bb@abbrev{Kentucky}{Ky.}
\bb@abbrev{Los Angeles}{L.A.}
\bb@abbrev{Louisiana}{La.}
\bb@abbrev{Maine}{Me.}
\bb@abbrev{Maryland}{Md.}
\bb@abbrev{Massachusetts}{Mass.}
\bb@abbrev{Michigan}{Mich.}
\bb@abbrev{Minnesota}{Minn.}
\bb@abbrev{Mississippi}{Miss.}
\bb@abbrev{Missouri}{Mo.}
\bb@abbrev{Montana}{Mont.}
\bb@abbrev{Nebraska}{Neb.}
\bb@abbrev{Nevada}{Nev.}
\bb@abbrev{New Hampshire}{N.H.}
\bb@abbrev{New Jersey}{N.J.}
\bb@abbrev{New Mexico}{N.M.}
\bb@abbrev{New York}{N.Y.}
\bb@abbrev{North Carolina}{N.C.}
\bb@abbrev{North Dakota}{N.D.}
\bb@abbrev{Northern Mariana Islands}{N. Mar. I.}
\bb@abbrev{Oklahoma}{Okla.}
\bb@abbrev{Oregon}{Or.}
\bb@abbrev{Pennsylvania}{Pa.}
\bb@abbrev{Philadelphia}{Phila.}
\bb@abbrev{Puerto Rico}{P.R.}
\bb@abbrev{Rhode Island}{R.I.}
\bb@abbrev{South Carolina}{S.C.}
\bb@abbrev{South Dakota}{S.D.}
\bb@abbrev{San Francisco}{S.F.}
\bb@abbrev{Tennessee}{Tenn.}
\bb@abbrev{Texas}{Tex.}
\bb@abbrev{Vermont}{Vt.}
\bb@abbrev{Virgin Islands}{V.I.}
\bb@abbrev{Virginia}{Va.}
\bb@abbrev{Washington}{Wash.}
\bb@abbrev{West Virginia}{W. Va.}
\bb@abbrev{Wisconsin}{Wis.}
\bb@abbrev{Wyoming}{Wyo.}
%
% Australia
%
\bb@abbrev{New South Wales}{N.S.W.}
\bb@abbrev{Queensland}{Queensl.}
\bb@abbrev{Tasmania}{Tas.}
% XXX: We do not multi@abbreviate Victoria, as it is most likely not used as a state
% of Australia.
%
% Canada
%
\bb@abbrev{Alberta}{Alta.}
\bb@abbrev{British Columbia}{B.C.}
\bb@abbrev{Manitoba}{Man.}
\bb@abbrev{New Brunswick}{N.B.}
\bb@abbrev{Newfoundland}{Nfld.}
\bb@abbrev{Northwest Territories}{N.W.T.}
\bb@abbrev{Nova Scotia}{N.S.}
\bb@abbrev{Nunavut}{Nun.}
\bb@abbrev{Ontario}{Ont.}
\bb@abbrev{Prince Edward Island}{P.E.I.}
\bb@abbrev{Quebec}{Que.}
\bb@abbrev{Saskatchewan}{Sask.}
%
% Countries
%
\bb@abbrev{Afghanistan}{Afg.}
\bb@abbrev{Africa}{Afr.}
\bb@abbrev{Albania}{Alb.}
\bb@abbrev{Algeria}{Alg.}
\bb@abbrev{Angola}{Angl.}
\bb@abbrev{Antigua}{Ant.}
\bb@abbrev{Argentina}{Arg.}
\bb@abbrev{Armenia}{Arm.}
\bb@abbrev{Australia}{Austl.}
\bb@abbrev{Austria}{Aus.}
\bb@abbrev{Azerbajian}{Azer.}
\bb@abbrev{Bahamas}{Bah.}
\bb@abbrev{Bahrain}{Bahr.}
\bb@abbrev{Bangladesh}{Bangl.}
\bb@abbrev{Barbados}{Barb.}
\bb@abbrev{Barbuda}{Barb.}
\bb@abbrev{Belarus}{Belr.}
\bb@abbrev{Belgium}{Belg.}
\bb@abbrev{Bermuda}{Berm.}
\bb@abbrev{Bolivia}{Bol.}
\bb@abbrev{Bosnia}{Bosn.}
\bb@abbrev{Botswana}{Bots.}
\bb@abbrev{Brazil}{Braz.}
\bb@abbrev{Bulgaria}{Bulg.}
\bb@abbrev{Burkina Faso}{Burk. Faso}
\bb@abbrev{Canada}{Can.}
\bb@abbrev{Cayman Islands}{Cayman Is.}
\bb@abbrev{Central African Republic}{Cent. Afr. Rep.}
\bb@abbrev{Colombia}{Colom.}
\bb@abbrev{Croatia}{Croat.}
\bb@abbrev{Czech Republic}{Czech Rep.}
\bb@abbrev{Denmark}{Den.}
\bb@abbrev{Djibouti}{Djib.}
\bb@abbrev{Dominican Republic}{Dom. Rep.}
\bb@abbrev{El Salvador}{El Sal.}
\bb@abbrev{England}{Eng.}
\bb@abbrev{Equatorial Guinea}{Eq. Guinea}
\bb@abbrev{Eritrea}{Eri.}
\bb@abbrev{Estonia}{Est.}
\bb@abbrev{Ethiopia}{Eth.}
\bb@abbrev{Europe}{Eur.}
\bb@abbrev{Falkland Islands}{Falkland Is.}
\bb@abbrev{Federal Republic of Germany}{F.R.G.}
\bb@abbrev{Finland}{Fin.}
\bb@abbrev{France}{Fr.}
\bb@abbrev{Gambia}{Gam.}
\bb@abbrev{GeorgiaUSSR}{Geor.}
\bb@abbrev{Gibraltar}{Gib.}
\bb@abbrev{Great Britain}{Gr. Brit.}
\bb@abbrev{Greenland}{Green.}
\bb@abbrev{Grenada}{Gren.}
\bb@abbrev{Guadeloupe}{Guad.}
\bb@abbrev{Guatemala}{Guat.}
\bb@abbrev{Guyana}{Guy.}
\bb@abbrev{Herzegovina}{Herz.}
\bb@abbrev{Honduras}{Hond.}
\bb@abbrev{Hong Kong}{H.K.}
\bb@abbrev{Hungary}{Hung.}
\bb@abbrev{Iceland}{Ice.}
\bb@abbrev{Indonesia}{Indon.}
\bb@abbrev{Ireland}{Ir.}
\bb@abbrev{Israel}{Isr.}
\bb@abbrev{Jamaica}{Jam.}
\bb@abbrev{Kazakhstan}{Kaz.}
\bb@abbrev{Kyrgyzstan}{Kyrg.}
\bb@abbrev{Latvia}{Lat.}
\bb@abbrev{Lebanon}{Leb.}
\bb@abbrev{Liberia}{Liber.}
\bb@abbrev{Liechtenstein}{Liech.}
\bb@abbrev{Lithuania}{Lith.}
\bb@abbrev{Luxembourg}{Lux.}
\bb@abbrev{Macau}{Mac.}
\bb@abbrev{Macedonia}{Maced.}
\bb@abbrev{Madagascar}{Madag.}
\bb@abbrev{Malaysia}{Malay.}
\bb@abbrev{Marshall Islands}{Marsh. Is.}
\bb@abbrev{Martinique}{Mart.}
\bb@abbrev{Mexico}{Mex.}
\bb@abbrev{Micronesia}{Micr.}
\bb@abbrev{Moldova}{Mold.}
\bb@abbrev{Mongolia}{Mong.}
\bb@abbrev{Montenegro}{Mont.}
\bb@abbrev{Mozambique}{Mozam.}
\bb@abbrev{Myanmar}{Myan.}
\bb@abbrev{Namibia}{Namib.}
\bb@abbrev{Netherlands}{Neth.}
\bb@abbrev{New Zealand}{N.Z.}
\bb@abbrev{Nicaragua}{Nicar.}
\bb@abbrev{Nigeria}{Nig.}
\bb@abbrev{Norway}{Nor.}
\bb@abbrev{Pakistan}{Pak. }
\bb@abbrev{Panama}{Pan.}
\bb@abbrev{Papua New Guinea}{Papua N.G.}
\bb@abbrev{Paraguay}{Para.}
\bb@abbrev{People's Republic of China}{P.R.C.}
\bb@abbrev{Philippines}{Phil.}
\bb@abbrev{Pitcairn Island}{Pitcairn Is.}
\bb@abbrev{Poland}{Pol.}
\bb@abbrev{Portugal}{Port.}
\bb@abbrev{Romania}{Rom.}
\bb@abbrev{Russia}{Russ.}
\bb@abbrev{Scotland}{Scot.}
\bb@abbrev{Senegal}{Sen.}
\bb@abbrev{Serbia}{Serb.}
\bb@abbrev{Seychelles}{Sey.}
\bb@abbrev{Singapore}{Sing.}
\bb@abbrev{Slovakia}{Slovk.}
\bb@abbrev{Slovenia}{Slovn.}
\bb@abbrev{Solomon Islands}{Solom. Is.}
\bb@abbrev{Somalia}{Somal.}
\bb@abbrev{St. Vincent & the Grenadines}{St. Vincent}
%\bb@abbrev{St. Vincent \& the Grenadines}{St. Vincent}
\bb@abbrev{St. Vincent and the Grenadines}{St. Vincent}
\bb@abbrev{Suriname}{Surin.}
\bb@abbrev{Swaziland}{Swaz.}
%
% As of the 18th edition, United States is not treated specially.
\bb@abbrev{United States}{U.S.}
\bb@abbrev{United States of America}{U.S.}
