%
% Bluebook Table 1, Reporters and Courts.
%
%
% Supreme Court.
%
\bb@newrep{U.S.}{L. Ed.}{%
    U.S.%
}
\bb@newrep{U.S.}{S. Ct.}{%
    U.S.%
}
\bb@newrep{U.S.}{U.S.}{%
    U.S.%
}
\bb@newrep{U.S.}{U.S.L.W.}{%
    U.S.%
}
%
% Federal reporters.
%
\bb@newrep{}{B.R.}{%
    Bankr. C.D. Cal.,%
    Bankr. C.D. Ill.,%
    Bankr. D.D.C.,%
    Bankr. D. Conn,%
    Bankr. D. Alaska,%
    Bankr. D. Ariz.,%
    Bankr. D. Colo.,%
    Bankr. D. Dela.,%
    Bankr. D. Guam,%
    Bankr. D. Haw.,%
    Bankr. D. Idaho,%
    Bankr. D. Kan.,%
    Bankr. D. Mass.,%
    Bankr. D. Md.,%
    Bankr. D. Me.,%
    Bankr. D. Minn.,%
    Bankr. D. Mont.,%
    Bankr. D. Neb.,%
    Bankr. D. Nev.,%
    Bankr. D. Or.,%
    Bankr. D. Utah,%
    Bankr. D. Vt.,%
    Bankr. D. Wyo.,%
    Bankr. D.D.C.,%
    Bankr. D.N. Mar. I.,%
    Bankr. D.N.D.,%
    Bankr. D.N.H.,%
    Bankr. D.N.J.,%
    Bankr. D.N.M.,%
    Bankr. D.P.R.,%
    Bankr. D.R.I.,%
    Bankr. D.S.C.,%
    Bankr. D.S.D.,%
    Bankr. E.D. Ark.,%
    Bankr. E.D. Cal.,%
    Bankr. E.D. Ky.,%
    Bankr. E.D. La.,%
    Bankr. E.D. Mich.,%
    Bankr. E.D. Mo.,%
    Bankr. E.D. Okla.,%
    Bankr. E.D. Pa.,%
    Bankr. E.D. Tenn.,%
    Bankr. E.D. Tex.,%
    Bankr. E.D. Va.,%
    Bankr. E.D. Wash.,%
    Bankr. E.D. Wis.,%
    Bankr. E.D.N.Y.,%
    Bankr. E.D.S.C.,%
    Bankr. M.D. Ala.,%
    Bankr. M.D. Fla.,%
    Bankr. M.D. Ga.,%
    Bankr. M.D. La.,%
    Bankr. M.D. Pa.,%
    Bankr. M.D. Tenn.,%
    Bankr. M.D.S.C.,%
    Bankr. N.D. Ala.,%
    Bankr. N.D. Cal.,%
    Bankr. N.D. Fla.,%
    Bankr. N.D. Ga.,%
    Bankr. N.D. Ill.,%
    Bankr. N.D. Ind.,%
    Bankr. N.D. Iowa,%
    Bankr. N.D. Miss.,%
    Bankr. N.D. Ohio,%
    Bankr. N.D. Okla.,%
    Bankr. N.D. Tex.,%
    Bankr. N.D.W. Va.,%
    Bankr. N.D.N.Y.,%
    Bankr. S.D. Ala.,%
    Bankr. S.D. Cal.,%
    Bankr. S.D. Fla.,%
    Bankr. S.D. Ga.,%
    Bankr. S.D. Ill.,%
    Bankr. S.D. Ind.,%
    Bankr. S.D. Iowa,%
    Bankr. S.D. Miss.,%
    Bankr. S.D. Ohio,%
    Bankr. S.D. Tex.,%
    Bankr. S.D.W. Va.,%
    Bankr. S.D.N.Y.,%
    Bankr. W.D. Ark.,%
    Bankr. W.D. Ky.,%
    Bankr. W.D. La.,%
    Bankr. W.D. Mich.,%
    Bankr. W.D. Mo.,%
    Bankr. W.D. Okla.,%
    Bankr. W.D. Pa.,%
    Bankr. W.D. Tenn.,%
    Bankr. W.D. Tex.,%
    Bankr. W.D. Va.,%
    Bankr. W.D. Wash.,%
    Bankr. W.D. Wis.,%
    Bankr. W.D. Mo.,%
    Bankr. W.D.N.C.,%
    Bankr. W.D.N.Y.%
}
\bb@newrep{}{F.}{%
    10th Cir.,%
    11th Cir.,%
    1st Cir.,%
    2d Cir.,%
    3d Cir.,%
    4th Cir.,%
    5th Cir.,%
    6th Cir.,%
    7th Cir.,%
    8th Cir.,%
    9th Cir.,%
    Comm. Ct.,%
    Emerg. Ct. App.,%
    Fed. Cir.,%
    Temp. Emerg. Ct. App.%
}
\bb@newrep{}{F. Supp.}{%
    C.D. Cal.,%
    C.D. Ill.,%
    Bankr. D.D.C.,%
    D. Conn.,%
    Ct. Intl. Trade,%
    Cust. Ct.,%
    D. Alaska,%
    D. Ariz.,%
    D. Colo.,%
    D. Dela.,%
    D. Guam,%
    D. Haw.,%
    D. Idaho,%
    D. Kan.,%
    D. Mass.,%
    D. Md.,%
    D. Me.,%
    D. Minn.,%
    D. Mont.,%
    D. Neb.,%
    D. Nev.,%
    D. Or.,%
    D. Utah,%
    D. Vt.,%
    D. Wyo.,%
    D.D.C.,%
    D.N. Mar. I.,%
    D.N.D.,%
    D.N.H.,%
    D.N.J.,%
    D.N.M.,%
    D.P.R.,%
    D.R.I.,%
    D.S.C.,%
    D.S.D.,%
    E.D. Ark.,%
    E.D. Cal.,%
    E.D. Ky.,%
    E.D. La.,%
    E.D. Mich.,%
    E.D. Mo.,%
    E.D. Okla.,%
    E.D. Pa,%
    E.D. Tenn.,%
    E.D. Tex.,%
    E.D. Va.,%
    E.D. Wash.,%
    E.D. Wis.,%
    E.D.N.Y.,%
    E.D.S.C.,%
    J.P.M.L.,%
    M.D. Ala.,%
    M.D. Fla.,%
    M.D. Ga.,%
    M.D. La.,%
    M.D. Pa.,%
    M.D. Tenn.,%
    M.D.S.C.,%
    N.D. Ala.,%
    N.D. Cal.,%
    N.D. Fla.,%
    N.D. Ga.,%
    N.D. Ill.,%
    N.D. Ind.,%
    N.D. Iowa,%
    N.D. Miss.,%
    N.D. Ohio,%
    N.D. Okla.,%
    N.D. Tex.,%
    N.D.W. Va.,%
    N.D.N.Y.,%
    Reg. Rail Reorg. Ct.,%
    S.D. Ala.,%
    S.D. Cal.,%
    S.D. Fla.,%
    S.D. Ga.,%
    S.D. Ill.,%
    S.D. Ind.,%
    S.D. Iowa,%
    S.D. Miss.,%
    S.D. Ohio,%
    S.D. Tex.,%
    S.D.W. Va.,%
    S.D.N.Y.,%
    W.D. Ark.,%
    W.D. Ky.,%
    W.D. La.,%
    W.D. Mich.,%
    W.D. Mo.,%
    W.D. Okla.,%
    W.D. Pa.,%
    W.D. Tenn.,%
    W.D. Tex.,%
    W.D. Va.,%
    W.D. Wash.,%
    W.D. Wis.,%
    W.D. Mo.,%
    W.D.N.C.,%
    W.D.N.Y.%
}
%
% Miscellaneous Federal reporters.
%
\bb@newrep{Cust. Ct.}{Cust. Ct.}{%
    Cust. Ct.%
}
\bb@newrep{Ct. Intl. Trade}{Ct. Intl. Trade}{%
    Ct. Intl. Trade%
}
\bb@newrep{}{Cust. B. \& Dec.}{%
    Ct. Intl. Trade,%
    Cust. Ct.%
}
\bb@newrep{}{I.T.R.D. (BNA)}{%
    Ct. Intl. Trade,%
    Cust. Ct.%
}
\bb@newrep{Vet. App.}{Vet. App.}{%
    Vet. App.%
}
%
% West regional reporters.
%
\bb@newrep{}{A.}{%
    Conn.,%
    Conn. App.,%
    Conn. Cir.,%
    Conn. Super.,%
    D.C. App.,%
    D.C. Mun. App.,%
    Del.,%
    Del. Ch.,%
    Del. Fam.,%
    Del. Super. Ct.,%
    Md.,%
    Md. Spec. App.,%
    Me.,%
    N.H.,%
    N.J.,%
    N.J. Super. App. Div.,%
    N.J. Super. Ch. Div.,%
    N.J. Super. L. Div.,%
    Pa.,%
    Pa. Commw. Ct.,%
    Pa. Super. Ct.,%
    R.I.,%
    Vt.%
}
\bb@newrep{}{N.E.}{%
    Ill.,%
    Ill. App.,%
    Ind.,%
    Ind. App.,%
    Mass.,%
    Mass. App.,%
    N.Y.,%
    Ohio,%
    Ohio App.%
}
\bb@newrep{}{N.W.}{%
    Iowa,%
    Iowa App.,%
    Mich.,%
    Mich. App.,%
    Minn.,%
    Minn. App.,%
    N.D.,%
    N.D. App.,%
    Neb.,%
    Neb. App.,%
    S.D.,%
    Wis.,%
    Wis. App.%
}
\bb@newrep{}{P.}{%
    Alaska,%
    Alaska App.,%
    Ariz.,%
    Ariz. App.,%
    Cal.,%
    Cal. App.,%
    Cal. Dist. App.,%
    Cal. Super. App. Dept.,%
    Colo.,%
    Colo. App.,%
    Haw.,%
    Haw. App.,%
    Idaho,%
    Idaho App.,%
    Kan. App.,%
    Kans.,%
    Mont.,%
    N.M.,%
    N.M. App.,%
    Nev.,%
    Okla.,%
    Okla. App.,%
    Okla. Crim. App.,%
    Or.,%
    Or. App.,%
    Utah,%
    Utah App.,%
    Wash.,%
    Wash. App.,%
    Wyo.%
}
\bb@newrep{}{S.E.}{%
    Ga.,%
    N.C.,%
    N.C. App.,%
    S.C.,%
    S.C. App.,%
    Va.,%
    Va. Appeals,%
    W. Va.%
}
\bb@newrep{}{S.W.}{%
    Ark.,%
    Ark. App.,%
    Indian Terr.,%
    Ky.,%
    Ky. App.,%
    Mo.,%
    Mo. App.,%
    Tenn.,%
    Tenn. App.,%
    Tenn. Crim. App.,%
    Tex.,%
    Tex. App.,%
    Tex. Crim. App.%
}
\bb@newrep{}{So.}{%
    Ala.,%
    Ala. Civ. App.,%
    Ala. Crim. App.,%
    Fla.,%
    Fla. Dist. App.,%
    La.,%
    La. App.,%
    Miss.%
}
%
% State reporters.
%
\bb@newrep{Ala.}{Ala.}{%
    Ala.%
}
\bb@newrep{Ala.}{Ala. App.}{%
    Ala. Civ. App.,%
    Ala. Crim. App.%
}
\bb@newrep{Ariz.}{Ariz.}{%
    Ariz.,%
    Ariz. App.%
}
\bb@newrep{Ariz.}{Ariz. App.}{%
    Ariz. App.%
}
\bb@newrep{Ark.}{Ark.}{%
    Ark.,%
    Ark. App.%
}
\bb@newrep{Ark.}{Ark. App.}{%
    Ark. App.%
}
\bb@newrep{Cal.}{Cal.}{%
    Cal.%
}
\bb@newrep{Cal.}{Cal. App.}{%
    Cal. App.,%
    Cal. Dist. App.%
}
\bb@newrep{Cal.}{Cal. App. Supp.}{%
    Cal. Super. App. Dept.%
}
\bb@newrep{Cal.}{Cal. Rptr.}{%
    Cal.,%
    Cal. App.,%
    Cal. Super. App. Dept.%
}
\bb@newrep{Colo.}{Colo.}{%
    Colo.%
}
\bb@newrep{Colo.}{Colo. App.}{%
    Colo. App.%
}
\bb@newrep{Conn.}{Conn.}{%
    Conn.%
}
\bb@newrep{Conn.}{Conn. App.}{%
    Conn. App.%
}
\bb@newrep{Conn.}{Conn. Cir.}{%
    Conn. Cir.%
}
\bb@newrep{Conn.}{Conn. Supp.}{%
    Conn. Super.%
}
\bb@newrep{Del.}{Del.}{%
    Del.,%
    Del. Super. Ct.%
}
\bb@newrep{Del.}{Del. Ch.}{%
    Del. Ch.%
}
\bb@newrep{Fla.}{Fla.}{%
    Fla.%
}
\bb@newrep{Fla.}{Fla. Supp.}{%
    Fla. Cir.,%
    [Co.] County Ct.%
}
\bb@newrep{Ga.}{Ga.}{%
    Ga.%
}
\bb@newrep{Haw.}{Haw.}{%
    Haw.%
}
\bb@newrep{}{Haw. App.}{%
    Haw. App.%
}
\bb@newrep{}{Idaho}{%
    Idaho,%
    Idaho App.%
}
\bb@newrep{Ill.}{Ill.}{%
    Ill.%
}
\bb@newrep{Ill.}{Ill. App.}{%
    Ill. App.%
}
\bb@newrep{Ill.}{Ill. Cir.}{%
    Ill. Cir.%
}
\bb@newrep{Ill.}{Ill. Cl.}{%
    Ill. Cl.%
}
\bb@newrep{Ill.}{Ill. Dec.}{%
    Ill.,%
    Ill. App.%
}
\bb@newrep{Ind.}{Ind.}{%
    Ind.%
}
\bb@newrep{Ind.}{Ind. App.}{%
    Ind. App.%
}
\bb@newrep{}{Iowa}{%
    Iowa%
}
\bb@newrep{Kan.}{Kan.}{%
    Kans.%
}
\bb@newrep{Kan.}{Kan. App.}{%
    Kan. App.,%
    Kan. App.%
}
\bb@newrep{Ky.}{Ky.}{%
    Ky.%
}
\bb@newrep{La.}{La.}{%
    La.%
}
\bb@newrep{Mass.}{Mass.}{%
    Mass.%
}
\bb@newrep{Mass.}{Mass. App.}{%
    Mass. App.%
}
\bb@newrep{Mass.}{Mass. App. Dec.}{%
    Mass. Dist. AD*%
}
\bb@newrep{Mass.}{Mass. App. Div.}{%
    Mass. Dist. AD*%
}
\bb@newrep{Mass.}{Mass. Supp.}{%
    Mass. Dist. AD*%
}
\bb@newrep{Md.}{Md.}{%
    Md.%
}
\bb@newrep{Md.}{Md. App.}{%
    Md. Spec. App.%
}
\bb@newrep{Me.}{Me.}{%
    Me.%
}
\bb@newrep{Mich.}{Mich.}{%
    Mich.%
}
\bb@newrep{Mich.}{Mich. App.}{%
    Mich. App.%
}
\bb@newrep{Minn.}{Minn.}{%
    Minn.%
}
\bb@newrep{Miss.}{Miss.}{%
    Miss.%
}
\bb@newrep{Miss.}{Miss. Dec.}{%
    Miss.%
}
\bb@newrep{Mo.}{Mo.}{%
    Mo.%
}
\bb@newrep{Mo.}{Mo. App.}{%
    Mo. App.%
}
\bb@newrep{Mont.}{Mont.}{%
    Mont.%
}
\bb@newrep{N.C.}{N.C.}{%
    N.C.%
}
\bb@newrep{N.C.}{N.C. App.}{%
    N.C. App.%
}
\bb@newrep{N.D.}{N.D.}{%
    N.D.%
}
\bb@newrep{N.H.}{N.H.}{%
    N.H.%
}
\bb@newrep{N.J.}{N.J.}{%
    N.J.,%
    N.J. Ch.,%
    N.J. Prerog.%
}
\bb@newrep{N.J.}{N.J. Eq.}{%
    N.J.,%
    N.J. Super. App. Div.,%
    N.J. Super. Ch. Div.,%
    N.J. Super. L. Div.%
}
\bb@newrep{N.J.}{N.J. L.}{%
    N.J.,%
    N.J. Super. App. Div.,%
    N.J. Super. Ch. Div.,%
    N.J. Super. L. Div.%
}
\bb@newrep{N.J.}{N.J. Misc.}{%
    N.J.,%
    N.J. Super. App. Div.,%
    N.J. Super. Ch. Div.,%
    N.J. Super. L. Div.%
}
\bb@newrep{N.J.}{N.J. Super.}{%
    N.J. Super. App. Div.,%
    N.J. Super. Ch. Div.,%
    N.J. Super. L. Div.%
}
\bb@newrep{N.J.}{N.J. Tax}{%
    N.J. Tax%
}
\bb@newrep{N.M.}{N.M.}{%
    N.M.,%
    N.M. App.%
}
\bb@newrep{N.Y.}{N.Y.}{%
    N.Y.,%
    N.Y. Ch.,%
    N.Y. Errors%
}
\bb@newrep{N.Y.}{N.Y. Misc.}{%
    [Various]%
}
\bb@newrep{}{N.Y.S.}{%
    N.Y.,%
    N.Y. App. Div. 1st Dept.
    N.Y. App. Div. 2d Dept.
    N.Y. App. Div. 3d Dept.
    N.Y. App. Div. 4th Dept.
}
\bb@newrep{}{A.D.}{%
    N.Y. App. Div. 1st Dept.
    N.Y. App. Div. 2d Dept.
    N.Y. App. Div. 3d Dept.
    N.Y. App. Div. 4th Dept.
}
\bb@newrep{Neb.}{Neb.}{%
    Neb.%
}
\bb@newrep{Neb.}{Neb. App.}{%
    Neb. App.%
}
\bb@newrep{Nev.}{Nev.}{%
    Nev.%
}
\bb@newrep{Ohio}{Ohio App.}{%
    Ohio App.%
}
\bb@newrep{Ohio}{Ohio Misc.}{%
    [Various]%
}
\bb@newrep{Ohio}{Ohio Op.}{%
    [Various]%
}
\bb@newrep{Ohio}{Ohio St.}{%
    Ohio%
}
\bb@newrep{Okla.}{Okla.}{%
    Okla.%
}
\bb@newrep{Okla.}{Okla. Crim.}{%
    Okla. Crim. App.%
}
\bb@newrep{Or.}{Or.}{%
    Or.%
}
\bb@newrep{Or.}{Or. App.}{%
    Or. App.%
}
\bb@newrep{Or.}{Or. Tax}{%
    Or. Tax%
}
\bb@newrep{P.R.}{P.R. Off. Trans.}{%
    P.R.%
}
\bb@newrep{P.R.}{P.R. Sent.}{%
    P.R.%
}
\bb@newrep{Pa.}{Pa.}{%
    Pa.%
}
\bb@newrep{Pa.}{Pa. Commw.}{%
    Pa. Commw. Ct%
}
\bb@newrep{Pa.}{Pa. D. \& C.}{%
    Pa. [Co.] Ct.%
}
\bb@newrep{Pa.}{Pa. Super.}{%
    Pa. Super. Ct.%
}
\bb@newrep{R.I.}{R.I.}{%
    R.I.%
}
\bb@newrep{S.C.}{S.C.}{%
    S.C.,%
    S.C. App.%
}
\bb@newrep{S.D.}{S.D.}{%
    S.D.%
}
\bb@newrep{Tenn.}{Tenn.}{%
    Tenn.%
}
\bb@newrep{Tenn.}{Tenn. App.}{%
    Tenn. App.%
}
\bb@newrep{Tenn.}{Tenn. Crim.}{%
    Tenn. Crim. App.%
}
\bb@newrep{Tex.}{Tex.}{%
    Tex.%
}
\bb@newrep{Tex.}{Tex. Civ.}{%
    Tex. App.,%
    Tex. Civ. App.%
}
\bb@newrep{Tex.}{Tex. Crim.}{%
    Tex. App.,%
    Tex. Crim. App.%
}
\bb@newrep{Utah}{Utah}{%
    Utah%
}
\bb@newrep{Va.}{Va.}{%
    Va.%
}
\bb@newrep{Va.}{Va. Appeals}{%
    Va. Appeals%
}
\bb@newrep{Va.}{Va. Cir.}{%
    Va. Cir.%
}
\bb@newrep{Vt.}{Vt.}{%
    Vt.%
}
\bb@newrep{W. Va.}{W. Va.}{%
    W. Va.%
}
\bb@newrep{W. Va.}{W. Va. Cl.}{%
    W. Va. Cl.%
}
\bb@newrep{Wash.}{Wash.}{%
    Wash.%
}
\bb@newrep{Wash.}{Wash. App.}{%
    Wash. App.%
}
\bb@newrep{Wis.}{Wis.}{%
    Wis.,%
    Wis. App.%
}
\bb@newrep{Wyo.}{Wyo.}{%
    Wyo.%
}
%
%
% Territories.
%
% Oklahoma Court of Appeals of the Indian Territory.
\bb@newrep{}{Indian Terr.}{%
    Indian Terr.%
}
%
% Puerto Rico.
\bb@newrep{}{C.A.}{%
    P.R.%
}
\bb@newrep{P.R.}{D.P.R.}{%
    P.R.%
}
\bb@newrep{}{J.T.S.}{%
    P.R.%
}
\bb@newrep{P.R.}{P.R.R.}{%
    P.R.%
}
\bb@newrep{}{T.C.A.}{%
    P.R. Cir.%
}
\bb@newrep{P.R.}{T.S.P.R.}{%
    P.R.%
}
%
% American Samoa.
\bb@newrep{Am. Sam.}{Am. Sam.}{%
    Am. Sam.%
}
%
% Guam.
\bb@newrep{Guam}{Guam}{%
    D. Guam App. Div.%
}
%
% Navajo Nation.
\bb@newrep{Navajo}{Navajo Rptr.}{%
    Navajo,%
    Navajo D. Ct.%
}
%
% Northern Mariana Islands.
\bb@newrep{N. Mar. I.}{N. Mar. I.}{%
    N. Mar. I.%
}
\bb@newrep{N. Mar. I.}{N. Mar. I. Commw. Rptr.}{%
    D. N. Mar. I.,%
    N. Mar. I. Commw. Super. Ct.%
}
%
% Virgin Islands.
\bb@newrep{V.I.}{V.I.}{%
    V.I.%
}
%
%
\bb@newrep{}{A.B.R.}{%
    A.B.R.%
}
\bb@newrep{}{A.F.B.R.}{%
    A.F.B.R.%
}
\bb@newrep{}{B.T.A.}{%
    B.T.A.%
}
\bb@newrep{}{B.T.A.M. (CCH)}{%
    B.T.A.%
}
\bb@newrep{}{C.C.P.A.}{%
    Fed. Cir.%
}
\bb@newrep{}{C.G.B.R.}{%
    C.G.B.R.%
}
\bb@newrep{}{C.M.R.}{%
    A.C.M.R.,%
    A.F.C.M.R.,%
    C.A.A.F.,%
    C.G.C.M.R.,%
    N-M.C.M.R.%
}
\bb@newrep{}{Ct. Cl.}{%
    Ct. Cl.,%
    Fed. Cir.%
}
\bb@newrep{}{M.J.}{%
    A.C.M.R.,%
    A.F.C.M.R.,%
    C.A.A.F.,%
    C.G.C.M.R.,%
    N-M.C.M.R.%
}
\bb@newrep{}{C.M.A.}{%
    C.A.A.F.%
}
\bb@newrep{}{N-M.B.R.}{%
    N-M.B.R.%
}
\bb@newrep{}{T.C.}{%
    T.C.%
}
\bb@newrep{}{T.C.M. (CCH)}{%
    T.C.%
}
%
