\defcase{i4i}{
p=Microsoft Corp.,
d=i4i Limited Partnership,
cite=131/S. Ct./2238,
year=2011
}

\defcase{bilski}{
p=Bilski,
d=Kappos,
cite=130/S. Ct./3218,
year=2010
}

\defstatcode{35usc}{
cite=35/U.S.C./,
year=2013,
notoa
}

\defcase{quanta}{
p={Quanta Computer, Inc.},
d=LG Electronics Corp.,
cite=553/U.S./617,
year=2008
}

\defcase{funai}{
p=Funai Electric Co.,
d=Daiwoo Electronics Corp.,
cite=616/F.3d/1357,
court=Fed. Cir.,
year=2010
}
\defcase{katz}{
name=In re Katz Interactive Call Processing Litigation,
docket={2009-1450, -1451, -1452, -1468, -1469, 2010-1017},
netcase,
dbid=2011 U.S. App. LEXIS 3212,
date=Feb. 18{,} 2011
}

\defcase{rembrandt}{
p=Rembrandt Data Technologies{,} LP,
d=AOL{,} LLC,
cite=641/F.3d/1331,
court=Fed. Cir.,
date=2011
}
\defcase{cbt}{
p=CBT Flint Partners{,} LLC,
d={Return Path, Inc.},
cite=654/F.3d/1353,
court=Fed. Cir.,
year=2011
}
\defcase{htc}{
p=HTC Corp.,
d={IPCom GmbH \& Co., KG},
cite=667/F.3d/1270,
court=Fed. Cir.,
year=2012
}

\defcase{enzo}{
p={Enzo Biochem, Inc.},
d=Applera Corp.,
cite=599/F.3d/1325,
court=Fed. Cir.,
year=2010
}
\defcase{tti}{
p={Trading Technologies International, Inc.},
d={eSpeed, Inc.},
cite=595/F.3d/1340,
court=Fed. Cir.,
year=2010
}
\defcase{honeywell}{
p={Honeywell International, Inc.},
d={United States},
cite=596/F.3d/800,
court=Fed. Cir.,
year=2010
}
\defcase{hearing}{
p={Hearing Components, Inc.},
d={Shure Inc.},
cite=600/F.3d/1357,
court=Fed. Cir.,
year=2010
}
\defcase{spansion}{
p={Spansion, Inc.},
d={International Trade Commission},
cite=629/F.3d/1331,
court=Fed. Cir.,
year=2010
}
\defcase{wellman}{
p={Wellman, Inc.},
d={Eastman Chemical Co.},
cite=642/F.3d/1355,
court=Fed. Cir.,
year=2011
}
\defcase{starsci}{
p={Star Scientific, Inc.},
d=R.J. Reynolds Tobacco Co.,
cite=655/F.3d/1364,
court=Fed. Cir.,
year=2011
}
\defcase{dowchem}{
p=Dow Chemical Co.,
d=Nova Chemicals Corp. Canada,
cite=458/Fed. Appx./910,
court=Fed. Cir.,
year=2012
}
\defcase{ernieball}{
p={Ernie Ball, Inc.},
d={Earvana, LLC},
cite=502/Fed. Appx./971,
court=Fed. Cir.,
year=2013
}
\defcase{accentra}{
cite=500/Fed. Appx./922,
p={Accentra, Inc.},
d={Staples, Inc.},
court=Fed. Cir.,
year=2013
}
\defcase{haemonetics}{
p=Haemonetics Corp.,
d=Baxter Healthcare Corp.,
cite=607/F.3d/776,
court=Fed. Cir.,
year=2010
}
\defcase{teva}{
p={Teva Pharmaceuticals USA, Inc.},
d={Sandoz, Inc.},
cite=723/F.3d/1363,
court=Fed. Cir.,
year=2013
}
\defcase{deere}{
p=Deere \& Co.,
d=Bush Hog{,} LLC,
cite=703/F.3d/1349,
court=Fed. Cir.,
year=2012
}
\defcase{igt}{
p=IGT,
d={Bally Gaming International, Inc.},
cite=659/F.3d/1109,
year=2011
}
\defcase{powerone}{
p={Power-One, Inc.},
d={Artesyn Technologies, Inc.},
cite=599/F.3d/1343,
court=Fed. Cir.,
year=2010
}

\defjrnart{ouellette}{
author=Lisa Larrimore Ouellette,
title=Do Patents Disclose Useful Information?,
cite=25/Harv. J.L. \& Tech./545,
date=2012
}
\defjrnart{lemley}{
author=Mark A. Lemley,
title=The Myth of the Sole Inventor,
cite=110/Mich. L. Rev./709,
date=2012
}

\defconst{patent-clause}{
    name=the Patent Clause,
    page={art. 1, S 8, cl. 8}
}

\defjrnart{hartung}{
author=Kirk M. Hartung,
title=Claim Construction: Another Matter of Chance and Confusion,
cite=88/J. Pat. \& Trademark Off. Soc'y/831,
date=2006
}
\defcase{datamize}{
p={Datamize, LLC},
d={Plumtree Software, Inc.},
cite=417/F.3d/1342,
court=Fed. Cir.,
year=2005
}
\defcase{shimadzu}{
p=Electric  Storage Battery Co.,
d=Shimadzu,
cite=307/U.S./5,
year=1939
}
\defstatcode{frcp8d2}{
cite=/Fed. R. Civ. P./8(d)(2)
}

\defjrnart{laser}{
author=Christa J. Laser,
title=A Definite Claim On Claim Indefiniteness,
cite=10/Chi.-Kent J. Intell. Prop./25,
year=2010
}
\defcase{festo}{
p=Festo Corp.,
d=Shoketsu Kinzoku Kogyo Kabushiki Co.,
cite=535/U.S./722,
year=2002
}
\defcase{mcclain}{
    p=McClain,
    d=Ortmayer,
    cite=141/U.S./419,
    year=1891
}
\defcase{unitedcarbon}{
    p=United Carbon Co.,
    d=Binney and Smith Co.,
    cite=317/U.S./228,
    year=1942
}
\defcase{exxon}{
    p=Exxon Research and Engineering Co.,
    d=United States,
    cite=265/F.3d/1371,
    court=Fed. Cir.,
    year=2001,
    inline=Exxon Research
}
\defbook{ftcreport}{
    instauth=Federal Trade Commission,
    title=The Evolving IP Marketplace: Aligning Patent Notice and Remedies with
    Competition,
    year=2011
}
\defmagart{bessen-regulation}{
    author=James Bessen,
    author=Jennifer Ford,
    author=Michael J. Meurer,
    title=The Private and Social Costs of Patent Trolls,
    src=Regulation,
    date=Winter 2011--2012,
    page=26,
url=http://object.cato.org/sites/cato.org/files/serials/files/regulation/2012/5/v34n4-1.pdf
}
\defcase{markman}{
    p=Markman,
    d={Westview Instruments, Inc.},
    cite=517/U.S./370,
    year=1996
}
\defcase{markman-fc}{
sameparties=markman,
cite=52 F.3d 967,
enbanc,
court=Fed. Cir.,
year=1995,
subsequent=affirmed: markman
}
\defcase{ge}{
    p=General Electric Corp.,
    d=Wabash Appliance Corp.,
    cite=304/U.S./364,
    year=1938
}
\defcase{halliburton}{
    p={Halliburton Energy Services, Inc.},
    d=M-I LLC,
    cite=514/F.3d/1244,
    court=Fed. Cir.,
    year=2008
}
\defcase{pmc}{
    p={Personalized Media Communications, LLC},
    d=International Trade Commission,
    cite=161/F.3d/696,
    court=Fed. Cir.,
    year=1998
}
\defcase{atmel}{
    p=Atmel Corp.,
    d={Information Storage Devices, Inc.},
    cite=198/F.3d/1374,
    court=Fed. Cir.,
    year=1999
}
\defcase{white}{
    p=White,
    d=Dunbar,
    cite=119/U.S./47,
    year=1886
}
\defcasedoc{applera-sg}{
    docname=Brief for the United States as \emph{Amicus Curiae},
    p=Applera Corp.,
    d={Enzo Biochem, Inc.},
    docket=10-426,
    date=2011,
    cite=131/S. Ct./847,
    paren=Mem.
}
\defcase{biosig}{
    p={Biosig Instruments, Inc.},
    d={Nautilus, Inc.},
    cite=715/F.3d/891,
    court=Fed. Cir.,
    year=2013
}
\defjrnart{chiang}{
    author=Tun-Jen Chiang,
    title=Fixing Patent Boundaries,
    cite=108/Mich. L. Rev./523,
    year=2010
}
\defbook{bessen-book}{
    author=James Bessen,
    author=Michael J. Meurer,
    title={Patent Failure: How Judges, Bureaucrats, and Lawyers Put Innovators
    at Risk},
    year=2008
}
\defnewsart{segal}{
    author=David Segal,
    title={Has Patent, Will Sue: An Alert to Corporate America},
    journal=New York Times,
    page=BU1,
    date={July 14, 2013}
}
\defbook{ppi}{
    author={Phil Goldberg, Progressive Policy Institute},
    title=Stumping Patent Trolls on the Bridge to Innovation,
    year=2013
}
\defwebsite{weir}{
    url=http://www.robweir.com/blog/2009/08/how-not-to-read-patent.html,
    author=Rob Weir,
    title=How Not to Read a Patent,
    date={Aug. 13, 2009}
}
\defwebsite{steeves}{
    url=http://www.insidecounsel.com/2013/10/11/new-report-examines-the-economic-cost-of-patent-tr,
    title=New Report Examines the Economic Cost of Patent Trolls,
    author=Rich Steeves,
    date={Oct. 11, 2013},
    src=InsideCounsel
}
\defcase{lazare}{
    p={Lazare Kaplan International, Inc.},
    d={Photoscribe Technologies, Inc.},
    cite=628/F.3d/1359,
    court=Fed. Cir.,
    year=2010
}
\defjrnart{mulligan-lee}{
    jcite=68 New York University Annual Survey of American Law 289,
    title=Scaling the Patent System,
    author=Christina Mulligan,
    author=Timothy B. Lee,
    year=2012
}
\defpatent{627patent}{
    number={7480627},
    date={Oct. 10, 2000}
}
\defreg{cfr1-2}{
    cite=37 C.F.R. S 1.2,
    year=2013
}
\defreg{cfr1-133}{
    cite=37 C.F.R. S 1.133,
    year=2013
}
\defcase{phillips}{
p=Phillips,
d=AWH Corp.,
cite=415/F.3d/1303,
court=Fed. Cir.,
year=2005
}
\defcase{lemelson}{
p=Lemelson,
d={General Mills, Inc.},
cite=968/F.2d/1202,
year=1992,
court=Fed. Cir.
}
\defbook{mpep}{
    title=Manual of Patent Examining Procedure,
    instauth=United States Patent and Trademark Office,
    year=2012,
    edition={8th ed., 9th rev.},
    hereinafter=MPEP
}
\defwebsite{inventivestep-interview}{
    url=http://inventivestep.net/2012/04/30/interviews-with-patent-examiners/,
    title=Interviews with Patent Examiners,
    author=Matthew R. Osenga,
    date={Apr. 30, 2012}
}
\defwebsite{eff-comments}{
    instauth=Electronic Frontier Foundation,
    title=Comments of EFF on Enhancement of Quality of Software-Related Patents,
    date={Apr. 15, 2013},
    url=available at
    https://www.eff.org/files/eff_comments_on_enhancement_of_quality_of_software-related_patents.pdf,
}
\defwebsite{ipfrontline}{
    url={http://www.ipfrontline.com/depts/article.aspx?id=721&deptid=4},
    title=Interviewing Patent Examiners---Advantageous or Disastrous?,
    date={Feb. 15, 2006},
    author=Susan Lynch
}
\defcasedoc{wildtangent-brief}{
    url=available at
    http://www.publicknowledge.org/files/wildtangent-v-ultramercial-pk-amicus.pdf,
    docname=Brief of \emph{Amicus Curiae} Public Knowledge in Support of
Petitioner,
    docket=13-255,
    p={WildTangent, Inc.},
    d={Ultramercial, LLC},
    date={June 21, 2013}
}
\defcase{cybor}{
    p=Cybor Corp.,
    d={FAS Technologies, Inc.},
    cite=138 F.3d 1448,
    year=1998,
    court=Fed. Cir.
}
\defstatcode{cand-rules}{
    rep=Northern District of California Patent Local Rules,
    year=2009,
    url=available at http://www.cand.uscourts.gov/localrules/patent
}

\defcase{actavis}{
p=Federal Trade Commission,
d={Actavis, Inc.},
cite=133 S. Ct. 2223,
year=2013
}

\defwebsite{whygpl}{
title=Why Upgrade to GPLv3,
author=Richard Stallman,
date={July 29, 2013},
url=https://www.gnu.org/licenses/rms-why-gplv3.html
}
\defwebsite{gplv3}{
url=http://www.gnu.org/licenses/gpl.html,
title=The GNU General Public License v.3.0,
date={June 29, 2007}
}
\defpressrelease{doj-cptn}{
instauth=Department of Justice,
title=CPTN Holdings LLC and Novell Inc. Change Deal in Order to Address
Department of Justice's Open Source Concerns,
date={Apr. 20, 2011},
url=available at http://www.justice.gov/opa/pr/2011/April/11-at-491.html
}
\defjrnart{chien-sw}{
author=Colleen V. Chien,
title=Reforming Software Patents,
jcite=50 Houston Law Review 325,
year=2012,
url=available at
http://www.houstonlawreview.org/wp-content/uploads/2013/02/2-Chien.pdf
}
\defmagart{cduan-forbes}{
author=Charles Duan,
title=Patent Trolls Are The Economy-Suffocating Exception To The `No Free Lunch'
Rule,
date={Nov. 15, 2013},
src=Forbes,
url=http://www.forbes.com/sites/realspin/2013/11/15/patent-trolls-are-the-economy-suffocating-exception-to-the-no-free-lunch-rule/
}
\defjrnart{greenspoon}{
author=Robert P. Greenspoon,
title=Is the United States Finally Ready for a Patent Small Claims Court?,
jcite={10 Minnesota Journal of Law, Science and Technology 549},
date=2009,
url=available at
http://mjlst.umn.edu/prod/groups/ahc/@pub/@ahc/@mjlst/documents/asset/ahc_asset_366031.pdf
}
\defmagart{schrage}{
author=Michael Schrage,
title=Archaic Patent Laws Need to Be Rewritten,
date={Oct. 24, 1991},
journal=Los Angeles Times,
page=D1,
url=available at
http://articles.latimes.com/1991-10-24/business/fi-436_1_intellectual-property-protection
}
\defwebsite{patentprogress-guide}{
url=http://www.patentprogress.org/2013/11/19/patent-progresss-guide-to-patent-reform-legislation/,
title=Patent Progress's Guide to Patent Reform Legislation,
author=Matt Levy,
date={Nov. 19, 2013}
}
\defbook{chien-oti}{
author={Colleen V. Chien, New America Foundation},
title=Patent Assertion and Startup Innovation,
year=2013,
url=http://www.newamerica.net/publications/policy/patent_assertion_and_startup_innovation
}
\defjrnart{bessen-direct}{
author=James Bessen,
author=Michael J. Meurer,
title=The Direct Costs from NPE Disputes,
year=2014,
jcite=99/Cornell Law Review/,
forthcoming,
url=http://www.bu.edu/law/faculty/scholarship/workingpapers/revcov.html
}
\defmagart{mossoff-forbes}{
url=http://www.forbes.com/sites/realspin/2012/12/18/policy-debates-on-patents-should-focus-on-facts-not-rhetoric/,
author=Adam Mossoff,
title={Policy Debates on Patents Should Focus on Facts, Not Rhetoric},
date={Dec. 18, 2012},
journal=Forbes
}
\defbook{boldrin}{
author=Michele Boldrin,
author=David K. Levine,
title=Against Intellectual Monopoly,
year=2008,
url=available at http://www.dklevine.com/general/intellectual/againstfinal.htm
}
\defjrnart{dpl}{
author=Jason Schultz,
author=Jennifer M. Urban,
title={Protecting Open Innovation: The Defensive Patent License as a New
Approach to Patent Threats, Transaction Costs, and Tactical Disarmament},
jcite=26 Harvard Journal of Law and Technology 1,
year=2012,
url=available at http://jolt.law.harvard.edu/articles/pdf/v26/26HarvJLTech1.pdf
}
\defmagart{brodkin-red-hat}{
url=http://arstechnica.com/business/2012/02/how-red-hat-killed-its-core-productand-became-a-billion-dollar-business/,
title=How Red Hat Killed Its Core Product---And Became a Billion-Dollar
Business,
author=Jon Brodkin,
date={Feb. 28, 2012},
journal=Ars Technica
}
\defmagart{stiglitz}{
author=Joseph Stiglitz,
title=Give Prizes Not Patents,
journal=New Scientist,
date={Sept. 16, 2006},
page=21,
url=available at
http://www2.gsb.columbia.edu/faculty/jstiglitz/download/2006_New_Scientist.pdf
}
\defjrnart{kremer}{
author=Michael Kremer,
title=Patent Buyouts: A Mechanism for Encouraging Innovation,
cite=113 The Quarterly Journal of Economics 1137,
year=1998
}
\defbook{stallman}{
author=Richard M. Stallman,
title={Free Software, Free Society},
edition=2d,
year=2010,
url=available at http://www.gnu.org/doc/fsfs-ii-2.pdf
}
\defwebsite{nobel-will}{
author=Alfred Bernhard Nobel,
title=Alfred Nobel's Will,
date={Nov. 27, 1895},
url=http://www.nobelprize.org/alfred_nobel/will/will-full.html
}
\defjrnart{hayter}{
author=Earl W. Hayter,
title={The Patent System and Agrarian Discontent, 1875-1888},
jcite=34 The Mississippi Valley Historical Review 59,
year=1947
}
\defbook{benkler}{
title=The Wealth of Networks: How Social Production Transforms Markets and
Freedom,
author=Yochai Benkler,
year=2006,
url=available at http://www.benkler.org/Benkler_Wealth_Of_Networks.pdf
}
\defbook{cathedral-bazaar}{
title=The Cathedral and the Bazaar: Musings on Linux and Open Source by an
Accidental Revolutionary,
author=Eric S. Raymond,
year=2001,
edition=rev.
}

\defmagart{iam-troll}{
author=Joff Wild,
title=The Real Inventors of the Term ``Patent Troll'' Revealed,
url={http://www.iam-magazine.com/blog/detail.aspx?g=cff2afd3-c24e-42e5-aa68-a4b4e7524177},
src=Intellectual Asset Management,
date={Aug. 22, 2008},
}

\defcase{bonitoboats}{
p={Bonito Boats, Inc.},
d={Thunder Craft Boats, Inc.},
cite=489 U.S. 141,
year=1989
}

\defcase{chakrabarty}{
p=Diamond,
d=Chakrabarty,
inlinedefendant,
cite=447 U.S. 303,
year=1980
}

\defbook{foundersconst}{
editor=Philip B. Kurland,
editor=Ralph Lerner,
title=The Founders' Constitution,
year=1987
}

\defletter{jefferson-letter}{
author=Thomas Jefferson,
to=Isaac McPherson,
date={Aug. 13, 1813},
reprinted={3 foundersconst at article 1, S 8, clause 8, document 12},
url=available at
http://press-pubs.uchicago.edu/founders/documents/a1_8_8s12.html
}

\defcase{kewanee}{
p=Kewanee Oil Co.,
d=Bicron Corp.,
year=1974,
cite=416 U.S. 470
}

\defjrnart{osenga}{
author=Kirsten Osenga,
title=Linguistics and Patent Claim Construction,
year=2006,
jcite=38 Rutgers Law Journal 61
}

\defstatcode{cand-patrules}{
instauth=United States District Court for the Northern District of California,
cite=/Patent Local Rules/,
year=2009,
url=available at http://www.cand.uscourts.gov/localrules/patent
}

\defbook{mandel}{
author=Michael Mandel,
title=Where the Jobs Are: The App Economy,
year=2012
}
\defbook{pappas}{
author={Andreas Pappas, VisionMobile Ltd.},
title=App Economy Forecasts 2013--2016,
date=2013
}

\defjrnart{seltzer}{
author=Wendy Seltzer,
title=Software Patents and/or Software Development,
year=2013,
cite=78 Brooklyn L. Rev. 929,
url=available at
http://www.brooklaw.edu/~/media/PDF/LawJournals/BLR_PDF/blr_v78iii.ashx
}

\defjrnart{menell}{
author=Peter S. Menell,
title=Indirect Copyright Liability and Technological Innovation,
year=2009,
jcite=32 Columbia Journal of Law and the Arts 375
}

\defcase{eldred}{
p=Eldred,
d=Ashcroft,
cite=537 U.S. 186,
year=2003
}
\defcase{pennock}{
p=Pennock,
d=Dialogue,
cite=27 U.S. (2 Pet.) 1,
year=1829
}
\defjrnart{fromer}{
author=Jeanne C. Fromer,
title=Patent Disclosure,
jcite=94 Iowa Law Review 539,
year=2009
}
\defjrnart{denicolo}{
author=Vincenzo Denicol\`o,
author=Luigi Alberto Franzoni,
title=The Contract Theory of Patents,
jcite=23 International Review of Law and Economics 365,
year=2003,
url=available at http://www2.dse.unibo.it/franzoni/contract.pdf
}
\defcasedoc{checkpoint-brief}{
docname={Brief of \emph{Amici Curiae} Checkpoint Software, Inc., et al., in
Support of Respondents},
p=Alice Corp. Pty. Ltd.,
d=CLS Bank International,
court=U.S.,
year={Feb. 27, 2014},
docket=13-298,
url=available at http://www.americanbar.org/content/dam/aba/publications/supreme_court_preview/briefs-v3/13-298_resp_amcu_cs-etal.pdf
}

\defjrnart{eisenberg}{
author=Rebecca S. Eisenberg,
title=The Role of the FDA in Innovation Policy,
jcite=13 Michigan Telecommunications and Technology Law Review 345,
year=2007,
url=available at http://www.mttlr.org/volthirteen/eisenberg.pdf
}

\defjrnart{lemley-vc}{
author=Mark A. Lemley,
title=Reconceiving Patents in the Age of Venture Capital,
jcite=4 Journal of Small and Emerging Business Law 137,
year=2000
}

\defwebsite{ipwatchdog-cost}{
author=Gene Quinn,
title=The Cost of Obtaining a Patent in the US,
date={Jan. 28, 2011},
url=http://www.ipwatchdog.com/2011/01/28/the-cost-of-obtaining-patent/,
src=IPWatchdog
}

\defwebsite{wired-ycombinator}{
author=Steven Levy,
title=Y Combinator Is Boot Camp for Startups,
date={May 17, 2011},
src=Wired,
url=http://www.wired.com/magazine/2011/05/ff_ycombinator/
}

\defbook{ries}{
author=Eric Ries,
title=The Lean Startup: How Today's Entrepreneurs Use Continuous Innovation to
Create Radically Successful Businesses,
year=2011
}

\defwebsite{w3c-patent}{
title=W3C Patent Policy,
src=W3.org,
date={Feb. 5, 2004},
url=http://www.w3.org/Consortium/Patent-Policy-20040205/,
author=Daniel J. Weitzner
}

\defbook{rfc2235}{
author=Robert H. Zakon,
title=Request for Comments 2235: Hobbes' Internet Timeline,
year=1997,
url=http://tools.ietf.org/html/rfc2235
}

\defwebsite{tal}{
title=When Patents Attack!,
src=This American Life,
date={July 22, 2011},
url=http://www.thisamericanlife.org/radio-archives/episode/441/when-patents-attack,
}
\defpressrelease{osrm-linux}{
title={Results of First-Ever Linux Patent Review Announced, Patent Insurance
Offered by Open Source Risk Management},
date={Aug. 2, 2004},
url=http://www.osriskmanagement.com/press_releases/press_release_080204.pdf,
author={Karen Duffin, Bite Communications for OSRM}
}

\defcase{cls-enbanc}{
p=CLS Bank International,
d=Alice Corp.,
cite=717 F.3d 1269,
year=2013,
inline=CLS Bank,
court=Fed. Cir.,
enbanc,
subsequent=certiorari granted: cls-cert
}
\defcase{cls-cert}{
revparties=cls-enbanc,
year=2013,
cite=134 S. Ct. 734,
}

\defcase{rosuvastatin}{
name=In re Rosuvastatin Calcium Patent Litigation,
cite=703 F.3d 511,
court=Fed. Cir.,
year=2012
}
\defcase{whittemore}{
p=Whittemore,
d=Cutter,
year=1813,
cite=29 F. Cas. 1120,
court=C.C.D. Mass.
}

\defjrnart{eisenberg-exp}{
jcite=56 University of Chicago Law Review 1017,
title=Patents and the Progress of Science: Exclusive Rights and Experimental
Use,
author=Rebecca S. Eisenberg,
year=1989
}

\defjrnart{p2p}{
title={``Peer to Patent'': Collective Intelligence, Open Review, and Patent
Reform},
author=Beth Simone Noveck,
jcite=20 Harvard Journal of Law and Technology 123,
year=2006
}

\defpressrelease{p2p-pr}{
title=USPTO Launches Second Peer To Patent Pilot in Collaboration with New York
Law School,
author={Peter Pappas, United States Patent and Trademark Office},
date={Oct. 19, 2010},
url=http://www.uspto.gov/news/pr/2010/10_50.jsp
}

\defpressrelease{wh-crowdsourcing}{
title=Fact Sheet---Executive Actions: Answering the President's Call to
Strengthen Our Patent System and Foster Innovation,
instauth={Office of the Press Secretary, The White House},
date={Feb. 20, 2014},
hereinafter=White House Executive Actions,
url=http://www.whitehouse.gov/the-press-office/2014/02/20/fact-sheet-executive-actions-answering-president-s-call-strengthen-our-p
}

\defcase{ksr}{
parties=KSR International Co. v. Teleflex Inc.,
cite=550 U.S. 398,
year=2007,
inline=KSR
}
\defcase{graham}{
parties=Graham v. John Deere Co. of Kansas City,
cite=383 U.S. 1,
year=1966
}
\defcase{kinetic}{
parties={Kinetic Concepts, Inc. v. Smith \& Nephew, Inc.},
cite=688 F.3d 1342,
court=Fed. Cir.,
year=2012
}

\defwebsite{twitter-license}{
title=Introducing the Innovator's Patent Agreement,
author=Adam Messinger,
src=The Official Twitter Blog,
date={Apr. 17, 2012},
url=https://blog.twitter.com/2012/introducing-innovators-patent-agreement
}

\defcasedoc{nautilus-brief}{
docname=Brief of Public Knowledge and the Electronic Frontier Foundation as
\emph{Amici Curiae} in Support of Petitioner,
parties={Nautilus, Inc. v. Biosig Instruments, Inc.},
court=U.S.,
date={Oct 23, 2013},
docket=13-369
}

\defwebsite{glossary-comments}{
url=http://www.uspto.gov/patents/init_events/swglossary_a_eff_2013oct24.pdf,
title=Comments of Public Knowledge and the Electronic Frontier Foundation on the
United States Patent and Trademark Office Software Partnership Meeting,
date={Oct. 24, 2013},
author=Charles Duan
}
\defjrnart{moore}{
author=Mark A. Lemley,
author=Kimberly A. Moore,
title=Ending Abuse of Patent Continuations,
year=2004,
jcite=84 Boston University Law Review 63
}
\defbookpart{shapiro}{
title={Navigating the Patent Thicket: Cross Licenses, Patent Pools, and Standard
Setting},
author=Carl Shapiro,
in=jaffe,
vol=1,
page=119
}
\defbook{jaffe}{
title=Innovation Policy and the Economy,
editor=Adam B. Jaffe,
editor=Josh Lerner,
editor=Scott Stern,
year=2001,
}
\defcase{tafas-settlement}{
parties=Tafas v. Kappos,
cite=586 F.3d 1369,
court=Fed. Cir.,
year=2009
}
\defcase{tafas}{
parties=Tafas v. Doll,
cite=559 F.3d 1345,
court=Fed. Cir.,
year=2009
}

\defjrnart{sheremetyeva}{
author=Svetlana Sheremetyeva,
title=Natural Language Analysis of Patent Claims,
year=2003,
jcite=20 Proceedings of the ACL-2003 Workshop on Patent Corpus Processing 66,
url=available at http://acl.ldc.upenn.edu/W/W03/W03-2008.pdf
}

\defwebsite{scanner-troll}{
url=http://arstechnica.com/tech-policy/2013/01/patent-trolls-want-1000-for-using-scanners/,
title={Patent Trolls Want \$1,000---for Using Scanners},
author=Joe Mullin,
date={Jan. 2, 2013},
src=Ars Technica
}
\defwebsite{lodsys}{
url=http://www.macrumors.com/2011/05/13/lodsys-threatens-to-sue-app-store-developers-over-purchase-links/,
title=Lodsys Threatens to Sue App Store Developers Over In-App Purchases and
Upgrade Links,
author=Erik Slivka,
date={May 13, 2011},
src=MacRumors
}
\defwebsite{innovatio}{
url=http://www.pcworld.com/article/2095700/cisco-reaches-agreement-with-innovatio-over-wifi-patents.html,
title=Cisco Reaches Agreement with Innovatio over Wi-Fi Patents,
author=John Ribeiro,
date={Feb. 7, 2014},
src=PCWorld
}
\defcase{precisionco}{
parties=Precision Instrument Manufacturing Co. v. Automotive Maintenance
Machinery Co.,
cite=324 U.S. 806,
year=1945
}
\defcase{walkerprocess}{
parties={Walker Process Equipment, Inc. v. Food Machinery \& Chemical Corp.},
cite=382 U.S. 172,
year=1965
}

\defjrnart{lemley-holdup}{
title=Patent Holdup and Royalty Stacking,
author=Mark A. Lemley,
author=Carl Shapiro,
url=http://faculty.haas.berkeley.edu/shapiro/stacking.pdf,
jcite=85 Texas Law Review 1991,
year=2007
}

\defjrnart{lemley-sep}{
author=Mark A. Lemley,
author=Carl Shapiro,
title=A Simple Approach to Setting Reasonable Royalties for Standard-Essential
Patents,
jcite=28 Berkeley Technology Law Journal 1135,
year=2013
}

\defbook{ftc-doj}{
instauth=United States Department of Justice,
instauth=Federal Trade Commission,
title=Antitrust Enforcement and Intellectual Property Rights: Promoting
Innovation and Competition,
year=2007,
url=available at http://www.usdoj.gov/atr/public/hearings/ip/222655.pdf
}
\defjrnart{hovenkamp}{
title=Consumer Welfare In Competition And Intellectual Property Law,
author=Herbert Hovenkamp,
year=2013,
jcite=9 Competition Policy International 53
}
\defbook{pwc}{
title={2013 Patent Litigation Study: Big Cases Make Headlines, While Patent
Cases Proliferate},
instauth=PricewaterhouseCoopers,
year=2013,
url=available at
http://www.pwc.com/en_us/us/forensic-services/publications/assets/2013-patent-litigation-study.pdf
}

\defjrnart{hemel}{
author=Daniel J. Hemel,
author=Lisa Larrimore Ouellette,
title=Beyond the Patents---Prizes Debate,
jcite=92 Texas Law Review 304,
year=2013,
url=available at http://www.texaslrev.com/wp-content/uploads/HemelOuellette.pdf
}

\defwebsite{cnet-aipla}{
author=Jim Kerstetter,
title=How Much Is that Patent Lawsuit Going to Cost You?,
date={Apr. 5, 2014},
src=CNet News,
url=http://news.cnet.com/8301-32973_3-57409792-296/how-much-is-that-patent-lawsuit-going-to-cost-you/
}

\deffedreg{uspto-ipd}{
title={Changes to Implement Inter Partes Review Proceedings, Post-Grant Review
Proceedings, and Transitional Program for Covered Business Method Patents},
cite={77 Fed. Reg. 48,680},
codified=37 C.F.R. part 42,
year=2012
}

\defstatsess{aia}{
title=America Invents Act,
cite=125 Stat. 284,
year=2011,
number=112-29
}

\defwebsite{southard}{
title=Economics and Logic of Patent Litigation Versus Post Grant/Inter Partes
Patent Review,
author=Thomas G. Southard,
author=Paul F. Prestia,
date={Oct. 3, 2012},
url={available at http://ratnerprestia.com/220?article=485},
src=RatnerPrestia
}

\defjrnart{moore-judges}{
author=Kimberly A. Moore,
title=Are District Court Judges Equipped to Resolve Patent Cases?,
jcite=15 Harvard Journal of Law and Technology 1,
year=2001
}

\defjrnart{moore-juries}{
author=Kimberly A. Moore,
title={Judges, Juries, and Patent Cases---An Empirical Peek Inside the Black
Box},
jcite=99 Michigan Law Review 365,
year=2000
}

\defcase{medimmune}{
parties={Medimmune, Inc. v. Genentech, Inc.},
cite=549 U.S. 118,
year=2007
}
\defcase{maryland-casualty}{
parties=Maryland Casualty Co. v. Pacific Coal \& Oil Co.,
cite=312 U.S. 270,
year=1941
}
\defengstat{aus-patent}{
name=Patents Act 1990,
country=Australia,
url=available at http://www.austlii.edu.au/au/legis/cth/consol_act/pa1990109/,
}
\defstatcode{17usc}{
cite=17/U.S.C./,
year=2013,
notoa
}
\defbill{shield}{
bill=H.R. 845,
name=Saving High-Tech Innovators from Egregious Legal Disputes Act,
congress=113,
year=2013
}
\defbill{cornyn}{
name=Patent Abuse Reduction Act,
year=2013,
congress=113,
bill=S. 1013
}
\defbill{goodlatte}{
name=Innovation Act,
year={Dec. 9, 2013},
bill=H.R. 3309,
congress=113,
status=referred to Senate
}
\defbill{hatch}{
name=Patent Litigation Integrity Act,
bill=S. 1612,
year=2013,
congress=113,
}
\defwebsite{mershon-trolls}{
title=White House Aims to Undercut Patent Trolls,
author=Erin Mershon,
date={Feb. 20, 2014},
src=Politico,
url=http://www.politico.com/story/2014/02/white-house-rolls-out-patent-actions-103727.html
}
\defwebsite{swang}{
url=http://www.publicknowledge.org/news-blog/blogs/impact-patent-troll-demand-letters,
src=Public Knowledge,
author=Stephen Wang,
title=The Impact of Patent Troll Demand Letters,
date={Nov. 13, 2013}
}
\defjrnart{alw}{
title=Patent Quality and Settlement Among Repeat
Patent Litigants,
author=John R. Allison,
author=Mark A. Lemley,
author=Joshua Walker,
jcite=99 Georgetown Law Journal 677,
year=2011,
url=available at
http://georgetownlawjournal.org/files/pdf/99-3/AllisonLemleyWalker\%2520677-712.PDF
}
\defbook{gao-report}{
instauth=United States Government Accountability Office,
title=Intellectual Property: Assessing Factors that Affect Patent Infringement
Litigation Could Help Improve Patent Quality,
year=2013,
serial=GAO-13-465,
url=available at http://www.gao.gov/assets/660/657103.pdf
}
\defhearing{hec-testimony}{
name=The Impact of Patent Assertion Entities on Innovation and the Economy,
committee=House Subcommittee on Oversight and Investigations of the House
Committee on Energy and Commerce,
congress=113,
year=2013,
paren={statement of Charles Duan, Director, Patent Reform Project, Public
Knowledge},
url=available at http://docs.house.gov/meetings/IF/IF02/20131114/101483/HHRG-113-IF02-Wstate-DuanC-20131114.pdf,
hereinafter=PAE Hearing Testimony
}
\defmagart{vtne-ag}{
title=Vermont and Nebraska Attorneys General Take Patent Trolls Head On,
author={William H. Sorrell, Vermont Attorney General},
author={Jon Bruning, Nebraska Attorney General},
date={Oct. 29, 2013},
src=NAAGazette,
issuer={National Association of Attorneys General, Washington, D.C.},
url=available at http://www.naag.org/assets/files/pdf/gazette/7-9-10.Gazette.pdf
}
\deffedreg{ftc-study}{
cite={78 Fed. Reg. 61,352},
year={Oct. 3, 2013},
title={Agency Information Collection Activities; Proposed Collection; Comment
Request},
instauth=Federal Trade Commission
}

\defstatcode{frcp}{
src=Fed. R. Civ. P.
}

\defcase{k-tech}{
parties=K-Tech Telecommunications v. Time Warner Cable,
cite=714 F.3d 1277,
court=Fed. Cir.,
year=2013
}
\defwebsite{patentlyo-twombly}{
url=http://patentlyo.com/patent/2013/04/federal-circuit-supports-bare-bones-patent-complaints.html,
title=Federal Circuit Supports Bare-Bones Patent Complaints,
date={Apr. 23, 2013},
src=Patently-O,
author=Dennis Crouch
}
\defcase{twombly}{
parties=Bell Atlantic Corp. v. Twombly,
cite=550 U.S. 544,
year=2007
}
\defcase{macronix}{
parties=Macronix International Co. v. Spansion Inc.,
dbid=2014 U.S. Dist. LEXIS 31465,
netcase,
date={Mar. 10, 2014},
court=E.D. Va.,
docket=3:13-cv-679,
url={available at http://scholar.google.com/scholar_case?case=5992875037084942788}
}
\defsecfiling{rpx}{
instauth=RPX Corporation,
title=Registration Statement,
number=S-1,
date={Sept. 2, 2011}
}
\defjrnart{layne-farrar}{
author=Anne Layne-Farrar,
author=A. Jorge Padilla,
author=Richard Schmalensee,
title=Pricing Patents for Licensing in Standard-Setting Organizations: Making
Sense of FRAND Commitments,
year=2007,
jcite=74 Antitrust Law Journal 671
}
\defwebsite{doj-uspto}{
url=http://www.justice.gov/atr/public/guidelines/290994.pdf,
instauth=U.S. Department of Justice,
instauth=U.S. Patent and Trademark Office,
title=Policy Statement on Remedies for Standards-Essential Patents Subject to
Voluntary F/RAND Commitments,
date={Jan. 8, 2013}
}
\defwebsite{balto}{
author=David Balto,
title=Using the Antitrust Laws to Police Patent Privateering,
date={June 3, 2013},
src=Patently-O,
url=http://patentlyo.com/patent/2013/06/guest-post-on-using-the-antitrust-laws-to-police-patent-privateering.html
}

\defwebsite{lee}{
author=Timothy B. Lee,
title=The Supreme Court Could Abolish Software Patents Next Year. Here's Why It
Should,
url=http://www.washingtonpost.com/blogs/the-switch/wp/2013/12/06/the-supreme-court-could-abolish-software-patents-next-year-heres-why-it-should/,
date=dec 6 2013,
src=Washington Post: The Switch
}

\defwebsite{bessen-switch}{
author=James Bessen,
date=sep 3 2013,
title=The Patent Troll Crisis Is Really a Software Patent Crisis,
src=Washington Post: The Switch,
url=http://www.washingtonpost.com/blogs/the-switch/wp/2013/09/03/the-patent-troll-crisis-is-really-a-software-patent-crisis/
}
\defbook{brynjolfsson}{
author=Erik Brynjolfsson,
author=Adam Saunders,
title=Wired for Innovation: How Information Technology Is Reshaping the Economy,
year=2010
}
\defwebsite{wee-3dp}{
url=http://www.cnbc.com/id/100942655,
title=The ``Gold Rush'' for 3-D Printing Patents,
author=Heesun Wee,
date=aug 15 2013,
url=CNBC.com
}
\defjrnart{burton}{
author=David A. Burton,
title=Software Developers Want Changes in Patent and Copyright Law,
jcite=3 Michigan Telecommunications and Technology Law Review 87,
year=1996,
url=http://www.mttlr.org/voltwo/burton.pdf,
}
\defjrnart{love}{
title=Expanding Patent Law's Customer Suit Exception,
author=Brian J. Love,
author=James C. Yoon,
jcite=93 Boston University Law Review 1605,
year=2013,
url=available at
http://www.bu.edu/bulawreview/files/2013/10/LOVE-YOON_Expanding-Patent.pdf
}
\defjrnart{chao}{
title=The Case for Contribution in Patent Law,
author=Bernard Chao,
jcite=80 University of Cincinnati Law Review 113,
year=2011,
url={http://scholarship.law.uc.edu/cgi/viewcontent.cgi?article=1083&context=uclr}
}
\defwebsite{long}{
author=David Long,
author=Matt Rizzolo,
date=sept 18 2013,
title=Protecting ``End Users'' from Patent Infringement Actions,
url=http://www.insidecounsel.com/2013/09/18/protecting-end-users-from-patent-infringement-acti,
src=InsideCounsel
}
\defwebsite{rackspace}{
title=Immunize End Users from Patent Trolls,
author=Alan Schoenbaum,
date=mar 19 2013,
url=http://www.rackspace.com/blog/immunize-end-users-from-patent-trolls/,
src=Rackspace Blog
}
\defwebsite{patentlyo-surplus}{
title=Capturing the Consumer Surplus Through Downstream Licensing and
Infringement Lawsuits,
author=Dennis Crouch,
url=http://patentlyo.com/patent/2013/12/capturing-the-consumer-surplus-through-downstream-licensing-and-infringement-lawsuits.html,
date=Dec 6 2013,
src=Patently-O
}
\defbill{farenthold}{
bill=H.R. 2639,
title=Patent Litigation and Innovation Act,
year=2013,
congress=113
}
\defbill{leahy}{
bill=S. 1720,
title=Patent Transparency and Improvements Act,
year=2013,
congress=113
}
\defcase{codex}{
parties=Codex Corp. v. Milgo Electronic Corp.,
cite=553 F.2d 735,
court=1st Cir.,
year=1977
}

\defcase{katz-v-lear}{
parties={Katz v. Lear Siegler, Inc.},
court=Fed. Cir.,
year=1990,
cite=909 F.2d 1459
}
\defwebsite{chien-patentlyo}{
author=Colleen Chien,
title=Patent Trolls by the Numbers,
date=mar 14 2013,
url=http://patentlyo.com/patent/2013/03/chien-patent-trolls.html,
src=Patently-O
}
\defjrnart{jarosz}{
author=John C. Jarosz,
author=Michael J. Chapman,
url=http://stlr.stanford.edu/pdf/royaltydamages.pdf,
title=The Hypothetical Negotiation and Reasonable Royalty Damages: The Tail
Wagging the Dog,
jcite=16 Stanford Technology Law Review 769,
year=2013
}
\defcase{uniloc}{
parties={Uniloc USA, Inc. v. Microsoft Corp.},
cite=632 F. 3d 1292,
court=Fed. Cir.,
year=2011
}
\defjrnart{seaman}{
url=http://www.law2.byu.edu/lawreview/archives/2010/5/05Seaman.pdf,
title=Reconsidering the \emph{Georgia-Pacific} Standard for Reasonable Royalty
Patent Damages,
author=Christopher B. Seaman,
jcite=/Brigham Young University Law Review/1661,
year=2010
}
\defcase{gp}{
parties=Georgia-Pacific Corp. v. U.S. Plywood Corp.,
cite=318 F. Supp. 1116,
court=S.D.N.Y.,
year=1970
}
\defmagart{adams-iam}{
author=Sara-Jayne Adams,
title=Quality Is the Key to a Bright Patent Future,
date=Apr./May 2008,
page=55,
journal=Intellectual Asset Management,
url={available at
http://www.iam-magazine.com/Issues/Article.ashx?g=7ec06ce7-8c64-4402-9222-f79e3aaaf171}
}
\defbook{ftc-2003}{
instauth=Federal Trade Commission,
title=To Promote Innovation: The Proper Balance of Competition and Patent Law
and Policy,
year=2003,
url=available at
http://www.ftc.gov/sites/default/files/documents/reports/promote-innovation-proper-balance-competition-and-patent-law-and-policy/innovationrpt.pdf
}
\defpressrelease{eff-podcasting}{
url=https://www.eff.org/press/releases/eff-files-challenge-patent-office-against-trolls-podcasting-patent,
title=EFF Files Challenge with Patent Office Against Troll's Podcasting Patent,
date=oct 16 2013,
instauth=Electronic Frontier Foundation,
}

\defcase{sony}{
parties={Sony Corp. of America v. Universal City Studios, Inc.},
cite=464 U.S. 417,
year=1984
}
\defjrnart{chafee}{
author={Zechariah Chafee, Jr.},
jcite=45 Columbia Law Review 503,
year=1945,
title=Reflections on the Law of Copyright: I
}
\defletter{newton}{
author=Isaac Newton,
to=Robert Hooke,
date=feb 5 1675,
url=available at
http://digitallibrary.hsp.org/index.php/Detail/Object/Show/object_id/9565
}
\defcase{funkbros}{
p=Funk Brothers Seed Co.,
d=Kalo Inoculant Co.,
cite=333 U.S. 127,
year=1948
}

\defcase{aptea}{
parties=Great Atlantic \& Pacific Tea Co. v. Supermarket Equipment Corp.,
year=1950,
cite=340 U.S. 147
}

\defwebsite{quality-comments}{
url=available at https://www.eff.org/files/2014/03/17/comments_to_pto_from_public_knowledge_eff_engine.pdf,
title={Comments of Public Knowledge, the Electronic Frontier Foundation, and
Engine Advocacy on Prior Art Resources for Use in the Examination of
Software-Related Patent Applications},
date=mar 17 2014,
author={Charles Duan, Public Knowledge},
}
\deffedreg{crowdsourcing-roundtable}{
title=Request for Comments and Notice of Roundtable Event on the Use of
Crowdsourcing and Third-Party Preissuance Submissions to Identify Relevant Prior
Art,
cite={79 Fed. Reg. 15,319},
year=2014,
instauth=United States Patent and Trademark Office
}
\defjrnart{lemley-forest}{
title=Missing the Forest for the Trolls,
author=Mark A. Lemley,
author=Douglas Melamed,
jcite=113 Columbia Law Review 2117,
year=2013,
url=available at
http://columbialawreview.org/missing-the-forest-for-the-trolls-3/
}
\defjrnart{harkins}{
title=Fending Off Paper Patents and Patent Trolls: A Novel ``Cold Fusion''
Defense Because Changing Times Demand It,
author=Christopher A. Harkins,
year=2007,
jcite=17 Albany Law Journal of Science and Technology 407,
url=available at http://www.brinksgilson.com/files/219.pdf
}
\defwebsite{mossoff-myth}{
author=Adam Mossoff,
title=The Myth of the ``Patent Troll'' Litigation Explosion,
date=aug 12 2013,
src=Center for the Protection of Intellectual Property,
url=http://cpip.gmu.edu/2013/08/12/the-myth-of-the-patent-troll-litigation-explosion/
}
\defjrnart{chien-arms}{
title=From Arms Race to Marketplace: The Complex Patent Ecosystem and Its
Implications for the Patent System ,
author=Colleen V. Chien,
year=2010,
jcite=62 Hastings Law Journal 297,
url=available at
http://www.hastingslawjournal.org/wp-content/uploads/2011/02/Chien_62-HLJ-297.pdf
}
\defjrnart{jeruss}{
url=available at http://scholarship.law.duke.edu/dltr/vol11/iss2/6/,
title=The America Invents Act 500: Effects of Patent Monetization Entities on US
Litigation,
author=Sara Jeruss,
author=Robin Feldman,
author=Joshua Walker,
jcite=11 Duke Law and Technology Review 357,
year=2012
}
\defjrnart{duffy}{
title=Reviving the Paper Patent Doctrine,
author=John F. Duffy,
jcite=98 Cornell Law Review 1359,
year=2013,
url=available at http://cornelllawreview.org/files/2013/10/98CLR1359.pdf
}
\defcase{ebay}{
parties={eBay Inc. v. MercExchange, LLC},
cite=547 U.S. 388,
year=2006
}
